### 2020-03-25 paper/paper.tex
new file:   paper/naaclhlt2019.bbl 	modified:   paper/naaclhlt2019.sty 	modified:   paper/naaclhlt2019.tex 	new file:   paper/paper.tex 	new file:   proposal/acl_natbib.bst 	new file:   proposal/naaclhlt2019.sty 	new file:   proposal/proposal.bbl 	new file:   proposal/proposal.bib 	new file:   proposal/proposal.tex

%
% File naacl2019.tex
%
%% Based on the style files for ACL 2018 and NAACL 2018, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2019}
\usepackage{times}
\usepackage{latexsym}

\usepackage{url}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{Life-long NLU: Continual Learning of Downstream Natural Language Tasks}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  This document contains the instructions for preparing a camera-ready
  manuscript for the proceedings of NAACL-HLT 2019. The document itself
  conforms to its own specifications, and is therefore an example of
  what your manuscript should look like. These instructions should be
  used for both papers submitted for review and for final versions of
  accepted papers.  Authors are asked to conform to all the directions
  reported in this document.
\end{abstract}

\section{Credits}

This document has been adapted from the instructions
for earlier ACL and NAACL proceedings,
including 
those for ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
NAACL 2018 by Margaret Michell and Stephanie Lukin,
2017/2018 (NA)ACL bibtex suggestions from Jason Eisner,
ACL 2017 by Dan Gildea and Min-Yen Kan, 
NAACL 2017 by Margaret Mitchell, 
ACL 2012 by Maggie Li and Michael White, 
those from ACL 2010 by Jing-Shing Chang and Philipp Koehn, 
those for ACL 2008 by JohannaD. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
those for ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
those for ACL 2002 by Eugene Charniak and Dekang Lin, 
and earlier ACL and EACL formats.
Those versions were written by several
people, including John Chen, Henry S. Thompson and Donald
Walker. Additional elements were taken from the formatting
instructions of the {\em International Joint Conference on Artificial
  Intelligence} and the \emph{Conference on Computer Vision and
  Pattern Recognition}.

\section{Introduction}

The following instructions are directed to authors of papers submitted
to NAACL-HLT 2019 or accepted for publication in its proceedings. All
authors are required to adhere to these specifications. Authors are
required to provide a Portable Document Format (PDF) version of their
papers. \textbf{The proceedings are designed for printing on A4
paper.}

\section{General Instructions}

Manuscripts must be in two-column format.  Exceptions to the
two-column format include the title, authors' names and complete
addresses, which must be centered at the top of the first page, and
any full-width figures or tables (see the guidelines in
Subsection~\ref{ssec:first}). {\bf Type single-spaced.}  Start all
pages directly under the top margin. See the guidelines later
regarding formatting the first page.  The manuscript should be
printed single-sided and its length
should not exceed the maximum page limit described in Section~\ref{sec:length}.
Pages are numbered for  initial submission. However, {\bf do not number the pages in the camera-ready version}.

By uncommenting {\small\verb|\aclfinalcopy|} at the top of this 
 document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.  When you first create your submission on softconf, please fill in your submitted paper ID where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top.

The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.  
However, you should maintain space for names and addresses so that they will fit in the final (accepted) version.  The NAACL-HLT 2019 \LaTeX\ style will create a titlebox space of 2.5in for you when {\small\verb|\aclfinalcopy|} is commented out.

The author list for submissions should include all (and only) individuals who made substantial contributions to the work presented. Each author listed on a submission to NAACL-HLT 2019 will be notified of submissions, revisions and the final decision. No authors may be added to or removed from submissions to NAACL-HLT 2019 after the submission deadline.

\subsection{The Ruler}
The NAACL-HLT 2019 style defines a printed ruler which should be presented in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document without the provided
style files, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment the {\small\verb|\aclfinalcopy|} command in the document preamble.)

Reviewers: note that the ruler measurements do not align well with
lines in the paper -- this turns out to be very difficult to do well
when the paper contains many figures and equations, and, when done,
looks ugly. In most cases one would expect that the approximate
location will be adequate, although you can also use fractional
references ({\em e.g.}, the first paragraph on this page ends at mark $108.5$).

\subsection{Electronically-available resources}

NAACL-HLT provides this description in \LaTeX2e{} ({\small\tt naaclhlt2019.tex}) and PDF
format ({\small\tt naaclhlt2019.pdf}), along with the \LaTeX2e{} style file used to
format it ({\small\tt naaclhlt2019.sty}) and an ACL bibliography style ({\small\tt acl\_natbib.bst})
and example bibliography ({\small\tt naaclhlt2019.bib}).
These files are all available at
{\small\tt http://naacl2019.org/downloads/ naaclhlt2019-latex.zip}. 
 We
strongly recommend the use of these style files, which have been
appropriately tailored for the NAACL-HLT 2019 proceedings.

\subsection{Format of Electronic Manuscript}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's
Portable Document Format (PDF). PDF files are usually produced from
\LaTeX\ using the \textit{pdflatex} command. If your version of
\LaTeX\ produces Postscript files, you can convert these into PDF
using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
Adobe Distiller to generate PDF.

Please make sure that your PDF file includes all the necessary fonts
(especially tree diagrams, symbols, and fonts with Asian
characters). When you print or create the PDF file, there is usually
an option in your printer setup to include none, all or just
non-standard fonts.  Please make sure that you select the option of
including ALL the fonts. \textbf{Before sending it, test your PDF by
  printing it from a computer different from the one where it was
  created.} Moreover, some word processors may generate very large PDF
files, where each page is rendered as an image. Such images may
reproduce poorly. In this case, try alternative ways to obtain the
PDF. One way on some systems is to install a driver for a postscript
printer, send your document to the printer specifying ``Output to a
file'', then convert the file to PDF.

It is of utmost importance to specify the \textbf{A4 format} (21 cm
x 29.7 cm) when formatting the paper. When working with
{\tt dvips}, for instance, one should specify {\tt -t a4}.
Or using the command \verb|\special{papersize=210mm,297mm}| in the latex
preamble (directly below the \verb|\usepackage| commands). Then using 
{\tt dvipdf} and/or {\tt pdflatex} which would make it easier for some.

Print-outs of the PDF file on A4 paper should be identical to the
hardcopy version. If you cannot meet the above requirements about the
production of your electronic submission, please contact the
publication chairs as soon as possible.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted. The exact dimensions for a page on A4
paper are:

\begin{itemize}
\item Left and right margins: 2.5 cm
\item Top margin: 2.5 cm
\item Bottom margin: 2.5 cm
\item Column width: 7.7 cm
\item Column height: 24.7 cm
\item Gap between columns: 0.6 cm
\end{itemize}

\noindent Papers should not be submitted on any other paper size.
 If you cannot meet the above requirements about the production of 
 your electronic submission, please contact the publication chairs 
 above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's {\bf Times Roman} font should be
used. In \LaTeX2e{} this is accomplished by putting

\begin{quote}
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}
in the preamble. If Times Roman is unavailable, use {\bf Computer
  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
  10\% less dense than Adobe's Times Roman font.

\begin{table}[t!]
\begin{center}
\begin{tabular}{|l|rl|}
\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
document text & 11 pt  &\\
captions & 10 pt & \\
abstract text & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\end{center}
\caption{\label{font-table} Font guide. }
\end{table}

\subsection{The First Page}
\label{ssec:first}

Center the title, author's name(s) and affiliation(s) across both
columns. Do not use footnotes for affiliations. Do not include the
paper ID number assigned during the submission process. Use the
two-column format only when you begin the abstract.

{\bf Title}: Place the title centered at the top of the first page, in
a 15-point bold font. (For a complete guide to font sizes and styles,
see Table~\ref{font-table}) Long titles should be typed on two lines
without a blank line intervening. Approximately, put the title at 2.5
cm from the top of the page, followed by a blank line, then the
author's names(s), and the affiliation on the following line. Do not
use only initials for given names (middle initials are allowed). Do
not format surnames in all capitals ({\em e.g.}, use ``Mitchell'' not
``MITCHELL'').  Do not format title and section headings in all
capitals as well except for proper names (such as ``BLEU'') that are
conventionally in all capitals.  The affiliation should contain the
author's complete address, and if possible, an electronic mail
address. Start the body of the first page 7.5 cm from the top of the
page.

The title, author names and addresses should be completely identical
to those entered to the electronical paper submission website in order
to maintain the consistency of author information among all
publications of the conference. If they are different, the publication
chairs may resolve the difference without consulting with you; so it
is in your own interest to double-check that the information is
consistent.

{\bf Abstract}: Type the abstract at the beginning of the first
column. The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by about
0.6 cm on each side. Center the word {\bf Abstract} in a 12 point bold
font above the body of the abstract. The abstract should be a concise
summary of the general thesis and conclusions of the paper. It should
be no longer than 200 words. The abstract text should be in 10 point font.

{\bf Text}: Begin typing the main body of the text immediately after
the abstract, observing the two-column format as shown in the present document. Do not include page numbers.

{\bf Indent}: Indent when starting a new paragraph, about 0.4 cm. Use 11 points for text and subsection headings, 12 points for section headings and 15 points for the title.

\begin{table}
\centering
\small
\begin{tabular}{cc}
\begin{tabular}{|l|l|}
\hline
{\bf Command} & {\bf Output}\\\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\ 
\verb|{\.I}| & {\.I} \\ 
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\ 
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular} & 
\begin{tabular}{|l|l|}
\hline
{\bf Command} & {\bf  Output}\\\hline
\verb|{\c c}| & {\c c} \\ 
\verb|{\u g}| & {\u g} \\ 
\verb|{\l}| & {\l} \\ 
\verb|{\~n}| & {\~n} \\ 
\verb|{\H o}| & {\H o} \\ 
\verb|{\v r}| & {\v r} \\ 
\verb|{\ss}| & {\ss} \\\hline
\end{tabular}
\end{tabular}
\caption{Example commands for accented characters, to be used in, {\em e.g.}, \BibTeX\ names.}\label{tab:accents}
\end{table}

\subsection{Sections}

{\bf Headings}: Type and label section and subsection headings in the
style shown on the present document.  Use numbered sections (Arabic
numerals) in order to facilitate cross references. Number subsections
with the section number and the subsection number separated by a dot,
in Arabic numerals.
Do not number subsubsections.

\begin{table*}[t!]
\centering
\begin{tabular}{lll}
  output & natbib & previous ACL style files\\
  \hline
  \citep{Gusfield:97} & \verb|\citep| & \verb|\cite| \\
  \citet{Gusfield:97} & \verb|\citet| & \verb|\newcite| \\
  \citeyearpar{Gusfield:97} & \verb|\citeyearpar| & \verb|\shortcite| \\
\end{tabular}
\caption{Citation commands supported by the style file.
  The citation style is based on the natbib package and
  supports all natbib citation commands.
  It also supports commands defined in previous ACL style files
  for compatibility.
  }
\end{table*}

{\bf Citations}: Citations within the text appear in parentheses
as~\cite{Gusfield:97} or, if the author's name appears in the text
itself, as Gusfield~\shortcite{Gusfield:97}.
Using the provided \LaTeX\ style, the former is accomplished using
{\small\verb|\cite|} and the latter with {\small\verb|\shortcite|} or {\small\verb|\newcite|}. Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}; this is accomplished with the provided style using commas within the {\small\verb|\cite|} command, {\em e.g.}, {\small\verb|\cite{Gusfield:97,Aho:72}|}. Append lowercase letters to the year in cases of ambiguities.  
 Treat double authors as
in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two
authors are involved. Collapse multiple citations as
in~\cite{Gusfield:97,Aho:72}. Also refrain from using full citations
as sentence constituents.

We suggest that instead of
\begin{quote}
  ``\cite{Gusfield:97} showed that ...''
\end{quote}
you use
\begin{quote}
``Gusfield \shortcite{Gusfield:97}   showed that ...''
\end{quote}

If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
can use the command \verb|\citet| (cite in text)
to get ``author (year)'' citations.

If the Bib\TeX{} file contains DOI fields, the paper
title in the references section will appear as a hyperlink
to the DOI, using the hyperref \LaTeX{} package.
To disable the hyperref package, load the style file
with the \verb|nohyperref| option: \\{\small
\verb|\usepackage[nohyperref]{naaclhlt2019}|}

\textbf{Digital Object Identifiers}:  As part of our work to make ACL
materials more widely used and cited outside of our discipline, ACL
has registered as a CrossRef member, as a registrant of Digital Object
Identifiers (DOIs), the standard for registering permanent URNs for
referencing scholarly materials.  As of 2017, we are requiring all
camera-ready references to contain the appropriate DOIs (or as a
second resort, the hyperlinked ACL Anthology Identifier) to all cited
works.  Thus, please ensure that you use Bib\TeX\ records that contain
DOI or URLs for any of the ACL materials that you reference.
Appropriate records should be found for most materials in the current
ACL Anthology at \url{http://aclanthology.info/}.

As examples, we cite \cite{P16-1001} to show you how papers with a DOI
will appear in the bibliography.  We cite \cite{C14-1001} to show how
papers without a DOI but with an ACL Anthology Identifier will appear
in the bibliography.

As reviewing will be double-blind, the submitted version of the papers
should not include the authors' names and affiliations. Furthermore,
self-references that reveal the author's identity, {\em e.g.},
\begin{quote}
``We previously showed \cite{Gusfield:97} ...''  
\end{quote}
should be avoided. Instead, use citations such as 
\begin{quote}
``\citeauthor{Gusfield:97} \shortcite{Gusfield:97}
previously showed ... ''
\end{quote}

Any preliminary non-archival versions of submitted papers should be listed in the submission form but not in the review version of the paper. NAACL-HLT 2019 reviewers are generally aware that authors may present preliminary versions of their work in other venues, but will not be provided the list of previous presentations from the submission form.

\textbf{Please do not use anonymous citations} and do not include
 when submitting your papers. Papers that do not
conform to these requirements may be rejected without review.

\textbf{References}: Gather the full set of references together under
the heading {\bf References}; place the section before any Appendices. 
Arrange the references alphabetically
by first author, rather than by order of occurrence in the text.
By using a .bib file, as in this template, this will be automatically 
handled for you. See the \verb|\bibliography| commands near the end for more.

Provide as complete a citation as possible, using a consistent format,
such as the one for {\em Computational Linguistics\/} or the one in the 
{\em Publication Manual of the American 
Psychological Association\/}~\cite{APA:83}. Use of full names for
authors rather than initials is preferred. A list of abbreviations
for common computer science journals can be found in the ACM 
{\em Computing Reviews\/}~\cite{ACM:83}.

The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
American Psychological Association format, allowing regular citations, 
short citations and multiple citations as described above.

\begin{itemize}
\item Example citing an arxiv paper: \cite{rasooli-tetrault-2015}. 
\item Example article in journal citation: \cite{Ando2005}.
\item Example article in proceedings, with location: \cite{borsch2011}.
\item Example article in proceedings, without location: \cite{andrew2007scalable}.
\end{itemize}
See corresponding .bib file for further details.

Submissions should accurately reference prior and related work, including code and data. If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced. If multiple versions of a piece of prior work exist, the one used by the authors should be referenced. Authors should not rely on automated citation indices to provide accurate references for prior and related work.

{\bf Appendices}: Appendices, if any, directly follow the text and the
references (but see above).  Letter them in sequence and provide an
informative title: {\bf Appendix A. Title of Appendix}.

\subsection{Footnotes}

{\bf Footnotes}: Put footnotes at the bottom of the page and use 9
point font. They may be numbered or referred to by asterisks or other
symbols.\footnote{This is how a footnote should appear.} Footnotes
should be separated from the text by a line.\footnote{Note the line
separating the footnotes from the text.}

\subsection{Graphics}

{\bf Illustrations}: Place figures, tables, and photographs in the
paper near where they are first discussed, rather than at the end, if
possible.  Wide illustrations may run across both columns.  Color
illustrations are discouraged, unless you have verified that  
they will be understandable when printed in black ink.

{\bf Captions}: Provide a caption for every illustration; number each one
sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
Caption of the Table.''  Type the captions of the figures and 
tables below the body, using 10 point text. Captions should be placed below illustrations. Captions that are one line are centered (see Table~\ref{font-table}). Captions longer than one line are left-aligned (see Table~\ref{tab:accents}). Do not overwrite the default caption sizes. The naaclhlt2019.sty file is compatible with the caption and subcaption packages; do not add optional arguments.

\subsection{Accessibility}
\label{ssec:accessibility}

In an effort to accommodate people who are color-blind (as well as those printing
to paper), grayscale readability for all accepted papers will be
encouraged.  Color is not forbidden, but authors should ensure that
tables and figures do not rely solely on color to convey critical
distinctions. A simple criterion: All curves and points in your figures should be clearly distinguishable without color.

% Min: no longer used as of ACL 2018, following ACL exec's decision to
% remove this extra workflow that was not executed much.
% BEGIN: remove
%% \section{XML conversion and supported \LaTeX\ packages}

%% Following ACL 2014 we will also we will attempt to automatically convert 
%% your \LaTeX\ source files to publish papers in machine-readable 
%% XML with semantic markup in the ACL Anthology, in addition to the 
%% traditional PDF format.  This will allow us to create, over the next 
%% few years, a growing corpus of scientific text for our own future research, 
%% and picks up on recent initiatives on converting ACL papers from earlier 
%% years to XML.

%% We encourage you to submit a ZIP file of your \LaTeX\ sources along
%% with the camera-ready version of your paper. We will then convert them
%% to XML automatically, using the LaTeXML tool
%% (\url{http://dlmf.nist.gov/LaTeXML}). LaTeXML has \emph{bindings} for
%% a number of \LaTeX\ packages, including the ACL 2018 stylefile. These
%% bindings allow LaTeXML to render the commands from these packages
%% correctly in XML. For best results, we encourage you to use the
%% packages that are officially supported by LaTeXML, listed at
%% \url{http://dlmf.nist.gov/LaTeXML/manual/included.bindings}
% END: remove

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms
with appropriate transliterations and/or translations
since not all readers understand all such characters and terms.
Inline transliteration or translation can be represented in
the order of: original-form transliteration ``translation''.

\section{Length of Submission}
\label{sec:length}

The NAACL-HLT 2019 main conference accepts submissions of long papers and
short papers.
 Long papers may consist of up to eight (8) pages of
content plus unlimited pages for references. Upon acceptance, final
versions of long papers will be given one additional page -- up to nine (9)
pages of content plus unlimited pages for references -- so that reviewers' comments
can be taken into account. Short papers may consist of up to four (4)
pages of content, plus unlimited pages for references. Upon
acceptance, short papers will be given five (5) pages in the
proceedings and unlimited pages for references. 
For both long and short papers, all illustrations and tables that are part
of the main text must be accommodated within these page limits, observing
the formatting instructions given in the present document. Papers that do not conform to the specified length and formatting requirements are subject to be rejected without review.

NAACL-HLT 2019 does encourage the submission of additional material that is relevant to the reviewers but not an integral part of the paper. There are two such types of material: appendices, which can be read, and non-readable supplementary materials, often data or code.  Do not include this additional material in the same document as your main paper. Additional material must be submitted as one or more separate files, and must adhere to the same anonymity guidelines as the main paper. The paper must be self-contained: it is optional for reviewers to look at the supplementary material. Papers should not refer, for further detail, to documents, code or data resources that are not available to the reviewers. Refer to Appendix~\ref{sec:appendix} and Appendix~\ref{sec:supplemental} for further information.

Workshop chairs may have different rules for allowed length and
whether supplemental material is welcome. As always, the respective
call for papers is the authoritative source.

\section*{Acknowledgments}

The acknowledgments should go immediately before the references.  Do
not number the acknowledgments section. Do not include this section
when submitting your paper for review. \\

\noindent {\bf Preparing References:} \\
Include your own bib file like this:
\verb|\bibliographystyle{acl_natbib}|
\verb|\bibliography{naaclhlt2019}|

where \verb|naaclhlt2019| corresponds to a naaclhlt2019.bib file.
\bibliography{naaclhlt2019}
\bibliographystyle{acl_natbib}

\appendix

\section{Appendices}
\label{sec:appendix}
Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
Appendices should be {\bf uploaded as supplementary material} when submitting the paper for review. Upon acceptance, the appendices come after the references, as shown here. Use
\verb|\appendix| before any appendix section to switch the section
numbering over to letters.

\section{Supplemental Material}
\label{sec:supplemental}
Submissions may include non-readable supplementary material used in the work and described in the paper. Any accompanying software and/or data should include licenses and documentation of research review as appropriate. Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper. Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

Nonetheless, supplementary material should be supplementary (rather
than central) to the paper. {\bf Submissions that misuse the supplementary 
material may be rejected without review.}
Supplementary material may include explanations or details
of proofs or derivations that do not fit into the paper, lists of
features or feature templates, sample inputs and outputs for a system,
pseudo-code or source code, and data. (Source code and data should
be separate uploads, rather than part of the paper).

The paper should not rely on the supplementary material: while the paper
may refer to and cite the supplementary material and the supplementary material will be available to the
reviewers, they will not be asked to review the
supplementary material.

\end{document}

### 2020-03-25 proposal/proposal.tex
new file:   paper/naaclhlt2019.bbl 	modified:   paper/naaclhlt2019.sty 	modified:   paper/naaclhlt2019.tex 	new file:   paper/paper.tex 	new file:   proposal/acl_natbib.bst 	new file:   proposal/naaclhlt2019.sty 	new file:   proposal/proposal.bbl 	new file:   proposal/proposal.bib 	new file:   proposal/proposal.tex

%
% File naacl2019.tex
%
%% Based on the style files for ACL 2018 and NAACL 2018, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2019}
\usepackage{times}
\usepackage{latexsym}

\usepackage{url}

\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{Life-long NLU: Continual Learning of Downstream NLU Tasks}

\author{Mohith Damarapati, Govind Mittal, Chandra Prakash Konkimalla, Aakriti Gupta}
  % {\tt email@domain} \\\And
  % Second Author \\
  % Affiliation / Address line 1 \\
  % Affiliation / Address line 2 \\
  % Affiliation / Address line 3 \\
  % {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle

\vspace{-2cm}

\section{Problem Proposal}

Transformer based language models, like BERT, parallel human level performance in on several NLU tasks.  However, unlike humans, they need to be fine-tuned for each task separately and are prone to catastrophic forgetting like any other connectionist network. Our goal in this work is to investigate if we can enable language models to learn GLUE tasks in a continual learning fashion. We plan to show how serious the catastrophic forgetting problem is and explore approaches from continual learning literature to mitigate it.

\section{Background}

Natural cognitive systems gradually forget previously learned information unlike the catastrophic forgetting observed in current connectionist approaches \cite{french1999catastrophic}. This problem is significant in the domain of natural language understanding (NLU) as well.  Learning a new NLU task without forgetting previous task(s) is a significant problem that needs to be mitigated to achieve general linguistic intelligence. Experiments in Yogatama et al. [2] show that current state-of-the art (SOTA) language models like BERT \cite{DBLP:journals/corr/abs-1810-04805} still require considerable fine tuning on each task before they perform well. They suffer from catastrophic forgetting when trained on multiple tasks in a continual learning (CL) fashion.   Our goal in this work is to address this challenge and investigate approaches to mitigate the catastrophic forgetting problem.

A more recent language model ERNIE-2.0 \cite{DBLP:journals/corr/abs-1907-12412} which is pre-trained in a continual way performed better than BERT \cite{DBLP:journals/corr/abs-1810-04805} on downstream tasks.  This shows the importance of continual learning techniques in connectionist approaches.  Although similar to BERT 
\cite{DBLP:journals/corr/abs-1810-04805}, ERNIE-2.0 \cite{DBLP:journals/corr/abs-1907-12412} also needs to be fine-tuned on each of the NLU tasks separately and is prone to catastrophic forgetting.  We argue that after pre-training language models on such a huge corpus, they should possess the capability of learning multiple tasks in a sequential continual setting.  We plan to explore some of the continual strategies given in Parisi et al. \cite{DBLP:journals/corr/abs-1802-07569}.   Elastic Weight Consolidation \cite{DBLP:journals/corr/KirkpatrickPRVD16}, Memory Aware Synapses \cite{aljundi2018memory}, Gradient Episodic Memory \cite{DBLP:journals/corr/Lopez-PazR17} and Synaptic Intelligence \cite{DBLP:journals/corr/ZenkePG17} are the most notable ones.

We plan to show the magnitude of the catastrophic forgetting problem with the help of metrics like forward transfer, backward transfer and evaluation criteria.  Later, with the help of above mentioned techniques, we hope to improve and prevent negative backward transfer for different combinations of tasks. We will initially start by learning two GLUE tasks (i.e. learn a new task without forgetting the old task) with few continual learning techniques and can extend to more GLUE tasks.

\section{Code}
We will utilize code from two pre-trained language models: (1) \textbf{BERT} \cite{DBLP:journals/corr/abs-1810-04805} and (2) \textbf{ERNIE-2.0} \cite{DBLP:journals/corr/abs-1907-12412} and from four continual learning strategies: (1) \textbf{Elastic Weight Consolidation} \cite{EWC}, (2) \textbf{Gradient Episodic Memory} \cite{GEM}, (3) \textbf{Memory Aware Synapses} \cite{MAS}, and (4) \textbf{Synaptic Intelligence} \cite{SI}.

\section{Evaluation Metrics}
We will adopt the continual learning evaluation framework of Lopez-Paz et al. \cite{DBLP:journals/corr/Lopez-PazR17}.  We will evaluate and compare all above approaches based on three metrics -- Average Accuracy on all tasks, Backward Transfer to past tasks and Forward Transfer to future tasks.

\section{Data}
We propose to work in three phases, as follows:
\begin{itemize}
  \item \textbf{First Phase (Two low data tasks):} Microsoft Research Paraphrase Corpus (MRPC) (3.7k/1.7k) (paraphrase) and Recognizing Textual Entailment (2.5k/3k) (NLI)
  \item \textbf{Second Phase (Two high data tasks):} Quora Question Pairs and Mutli Natural Language Inference. 
  \item \textbf{Final Phase (All tasks):} More than two GLUE tasks (to be chosen later).
\end{itemize}

\bibliography{proposal}
\bibliographystyle{acl_natbib}

\end{document}

### 2020-03-25 proposal/proposal.tex
modified:   proposal/proposal.bbl 	modified:   proposal/proposal.bib 	modified:   proposal/proposal.tex

@@
 
-\title{Life-long NLU: Continual Learning of Downstream NLU Tasks}
+\title{Continual NLU: Enabling language models to learn downstream tasks in a continual way}
 
@@
 Experiments in Yogatama et al.
-[2] show that current state-of-the art (SOTA) language models like BERT \cite{DBLP:journals/corr/abs-1810-04805} still require considerable fine tuning on each task before they perform well.
+\cite{DBLP:journals/corr/abs-1901-11373} show that current state-of-the art (SOTA) language models like BERT \cite{DBLP:journals/corr/abs-1810-04805} still require considerable fine tuning on each task before they perform well.
 They suffer from catastrophic forgetting when trained on multiple tasks in a continual learning (CL) fashion.
@@
 \begin{itemize}
-  \item \textbf{First Phase (Two low data tasks):} Microsoft Research Paraphrase Corpus (MRPC) (3.7k/1.7k) (paraphrase) and Recognizing Textual Entailment (2.5k/3k) (NLI)
-  \item \textbf{Second Phase (Two high data tasks):} Quora Question Pairs and Mutli Natural Language Inference. 
+  \item \textbf{First Phase (Two low data tasks):} Microsoft Research Paraphrase Corpus (training - 3700 / testing - 1700) (paraphrase) and Recognizing Textual Entailment (training - 2500 / testing - 3000) (NLI).
+  \item \textbf{Second Phase (Two high data tasks):} GLUE: Quora Question Pairs and MutliNLI.
   \item \textbf{Final Phase (All tasks):} More than two GLUE tasks (to be chosen later).

### 2020-04-21 EWC/main.py
modified:   MAS/arguments.py 	new file:   MAS/dict_utils.py 	modified:   MAS/main.py 	new file:   MAS/mas_utils.py

@@ -15,7 +15,7 @@ from tqdm import tqdm, trange
 from collections import OrderedDict 
 
 from transformers import (
-    MODEL_FOR_SEQUENCE_CLASSIFICATION_MAPPING,
+    # MODEL_FOR_SEQUENCE_CLASSIFICATION_MAPPING,
     WEIGHTS_NAME,
     AdamW,
     AutoConfig,
@@ -333,7 +333,7 @@ def evaluate(args, model, task, tokenizer, accuracy_matrix, train_task_num, curr
 def load_and_cache_examples(args, task, tokenizer, evaluate=False):
 	processor = glue_processors[task]()
 	output_mode = glue_output_modes[task]
-	#data_size = 8 #To take low GPU memory 
+	#data_size = 8 #To take low GPU memory
 	logger.info("Creating features from dataset file at %s", args.data_dir)
 	label_list = processor.get_labels()
 	if task in ["mnli", "mnli-mm"] and args.model_type in ["roberta", "xlmroberta"]:
@@ -381,7 +381,7 @@ def main():
 	if args.n_gpu > 1:
 		model = torch.nn.DataParallel(model)
 
-	set_seed(args.seed, args.n_gpu)
+
 
 	# Prepare GLUE tasks
 	processors = {}

### 2020-04-21 MAS/arguments.py

@@ -51,6 +51,8 @@ def parse_args():
 						default=42,
 						type=int,
 						)
+	parser.add_argument('--init_lr', default=0.001, type=float, help='Initial learning rate for training the model')
+	parser.add_argument('--reg_lambda', default=0.01, type=float, help='Regularization parameter')
 
 	args = parser.parse_args()
 	with open(args.task_params) as file:

### 2020-04-21 MAS/main.py

@@ -30,10 +30,14 @@ try:
 except ImportError:
     from tensorboardX import SummaryWriter
 
-from utils import convert_dict
-from models.bert_finetuning import BertForContinualFineTuning
+from dict_utils import convert_dict
 
 from pdb import set_trace
+
+# MY IMPORTS
+from mas_utils import init_reg_params, shared_model, exp_lr_scheduler, compute_omega_grads_norm, \
+    init_reg_params_across_tasks, consolidate_reg_params
+from optimizer_lib import local_sgd, omega_update
 
 logger = logging.getLogger(__name__)
 logger.propagate = False
@@ -52,7 +56,7 @@ def save_model(args, task_num, model):
         os.makedirs(args.output_dir)
 
     task_paramters = OrderedDict()
-    bert_paramters = model.state_dict().copy()
+    bert_paramters = model.tmodel.state_dict().copy()
 
     for layer, weights in bert_paramters.items():
         if layer == "classifier.weight" or layer == 'classifier.bias':
@@ -62,43 +66,10 @@ def save_model(args, task_num, model):
 
     torch.save(bert_paramters, os.path.join(args.output_dir, "bert_paramters_" + str(task_num) + ".pt"))
     torch.save(task_paramters, os.path.join(args.output_dir, "task_paramters_" + str(task_num) + ".pt"))
-
+    torch.save(model.reg_params, os.path.join(args.output_dir, "reg_params_{}.pt".format(task_num)))
     print()
     print("***** Parameters Saved for task", task_num, "*****")
     print()
-
-
-def initialize_importance_params(model, freeze_layers=[]):
-    """initialize an omega for each parameter to zero"""
-    reg_params = {}
-    for name, param in model.named_parameters():
-        if not name in freeze_layers:
-            # print('initializing param', name)
-            omega = torch.FloatTensor(param.size()).zero_()
-            init_val = param.data.clone()
-            reg_param = {}
-            reg_param['omega'] = omega
-            # initialize the initial value to that before starting training
-            reg_param['init_val'] = init_val
-            reg_params[param] = reg_param
-    return reg_params
-
-
-def update_importance_params(train_dataset, fisher_sample_size, batch_size=32):
-
-def 
-
-def compute_mas_loss(model, lamda=0.1, consolidate_gradients,  ):
-    """Compute the MAS loss by using the Omega,  parameters and lambda"""
-    bert_parameters = model.state_dict().copy()
-    del bert_parameters["classifier.weight"]
[…]

### 2020-04-21 MAS/mas_utils.py

@@ -1,0 +1,211 @@
+import torch
+
+
+class shared_model(torch.nn.Module):
+
+    def __init__(self, model):
+        super(shared_model, self).__init__()
+        self.tmodel = model
+        self.reg_params = {}
+
+    def forward(self, x):
+        return self.tmodel(x)
+
+
+def init_reg_params(model, device, freeze_layers=['classifier.weight', 'classifier.bias']):
+    """
+    Input:
+    1) model: A reference to the model that is being trained
+    2) use_gpu: Set the flag to True if the model is to be trained on the GPU
+    3) freeze_layers: A list containing the layers for which omega is not calculated. Useful in the
+        case of computational limitations where computing the importance parameters for the entire model
+        is not feasible
+
+    Output:
+    1) model: A dictionary containing importance weights (omega), init_val (keep a reference
+    to the initial values of the parameters) for all trainable parameters is calculated and the updated
+    model with these reg_params is returned.
+
+
+    Function: Initializes the reg_params for a model for the initial task (task = 1)
+
+    """
+    reg_params = dict()
+    for name, param in model.tmodel.named_parameters():
+        if not name in freeze_layers:
+            print("Initializing omega values for layer", name)
+            omega = torch.zeros(param.size())
+            omega = omega.to(device)
+
+            init_val = param.data.clone()
+            param_dict = {}
+
+            # for first task, omega is initialized to zero
+            param_dict['omega'] = omega
+            param_dict['init_val'] = init_val
+
+            # the key for this dictionary is the name of the layer
+            reg_params[param] = param_dict
+
+    model.reg_params = reg_params
+
+    return model
+
+
+def exp_lr_scheduler(optimizer, epoch, init_lr=0.0008, lr_decay_epoch=20):
+    """
+    Decay learning rate by a factor of 0.1 every lr_decay_epoch epochs.
+
+    """
+    lr = init_lr * (0.1 ** (epoch // lr_decay_epoch))
+    # print('lr is ' + str(lr))
+
+    # if (epoch % lr_decay_epoch == 0):
+    #     print('LR is set to {}'.format(lr))
+
+    for param_group in optimizer.param_groups:
+        param_group['lr'] = lr
+
+    return optimizer
+
+
+def init_reg_params_across_tasks(model, device, freeze_layers=['classifier.weight', 'classifier.bias']):
+    """
+    Input:
+    1) model: A reference to the model that is being trained
[…]

### 2020-04-21 MAS/optimizer_lib.py
new file:   MAS/optimizer_lib.py

@@ -1,0 +1,218 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+from __future__ import print_function
+
+import torch
+import torch.nn as nn
+import torch.optim as optim
+
+import numpy as np
+import torchvision
+from torchvision import datasets, models, transforms
+
+import copy
+import os
+import shutil
+
+
+class local_sgd(optim.SGD):
+    def __init__(self, params, reg_lambda, lr=0.001, momentum=0, dampening=0, weight_decay=0, nesterov=False):
+        super(local_sgd, self).__init__(params, lr, momentum, dampening, weight_decay, nesterov)
+        self.reg_lambda = reg_lambda
+
+    def __setstate__(self, state):
+        super(local_sgd, self).__setstate__(state)
+
+    def step(self, reg_params, closure=None):
+
+        loss = None
+
+        if closure is not None:
+            loss = closure()
+
+        for group in self.param_groups:
+            weight_decay = group['weight_decay']
+            momentum = group['momentum']
+            dampening = group['dampening']
+            nesterov = group['nesterov']
+
+            for p in group['params']:
+
+                if p.grad is None:
+                    continue
+
+                d_p = p.grad.data
+
+                if p in reg_params:
+                    param_dict = reg_params[p]
+
+                    omega = param_dict['omega']
+                    init_val = param_dict['init_val']
+
+                    curr_param_value = p.data
+                    curr_param_value = curr_param_value.cuda()
+
+                    init_val = init_val.cuda()
+                    omega = omega.cuda()
+
+                    # get the difference
+                    param_diff = curr_param_value - init_val
+
+                    # get the gradient for the penalty term for change in the weights of the parameters
+                    local_grad = torch.mul(param_diff, 2 * self.reg_lambda * omega)
+
+                    del param_diff
+                    del omega
+                    del init_val
+                    del curr_param_value
+
+                    d_p = d_p + local_grad
+
+                    del local_grad
+
+                if (weight_decay != 0):
+                    d_p.add_(weight_decay, p.data)
+
+                if (momentum != 0):
+                    param_state = self.state[p]
+                    if 'momentum_buffer' not in param_state:
+                        buf = param_state['momentum_buffer'] = torch.clone(d_p).detach()
+                    else:
+                        buf = param_state['momentum_buffer']
+                        buf.mul_(momentum).add_(1 - dampening, d_p)
+                    if nesterov:
+                        d_p = d_p.add(momentum, buf)
+                    else:
+                        d_p = buf
+
[…]

### 2020-04-22 paper/paper.tex
modified:   MAS/main.py 	modified:   paper/paper.bbl 	modified:   paper/paper.bib 	modified:   paper/paper.tex

@@
 \begin{abstract}
-  This document contains the instructions for preparing a camera-ready
-  manuscript for the proceedings of NAACL-HLT 2019. The document itself
-  conforms to its own specifications, and is therefore an example of
-  what your manuscript should look like. These instructions should be
-  used for both papers submitted for review and for final versions of
-  accepted papers.  Authors are asked to conform to all the directions
-  reported in this document.
+  Qualified general intelligence has the ability of learning new tasks without immediately becoming worse at an older one.
+With this statement at the core of this paper, we explore various techniques to prevent forgetting in a state-of-the-art language model.
+These techniques range involve Elastic Weight Consolidation, Memory aware synapses and semantic intelligence \cite{french1999catastrophic}
 \end{abstract}
 
-\section{Credits}
+\bibliography{paper}
+\bibliographystyle{acl_natbib}
 
-This document has been adapted from the instructions
-for earlier ACL and NAACL proceedings,
-including 
-those for ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
-NAACL 2018 by Margaret Michell and Stephanie Lukin,
-2017/2018 (NA)ACL bibtex suggestions from Jason Eisner,
-ACL 2017 by Dan Gildea and Min-Yen Kan, 
-NAACL 2017 by Margaret Mitchell, 
-ACL 2012 by Maggie Li and Michael White, 
-those from ACL 2010 by Jing-Shing Chang and Philipp Koehn, 
-those for ACL 2008 by JohannaD. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
-those for ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
-those for ACL 2002 by Eugene Charniak and Dekang Lin, 
-and earlier ACL and EACL formats.
-Those versions were written by several
-people, including John Chen, Henry S. Thompson and Donald
-Walker. Additional elements were taken from the formatting
-instructions of the {\em International Joint Conference on Artificial
-  Intelligence} and the \emph{Conference on Computer Vision and
-  Pattern Recognition}.
+% \section{Credits}
 
-\section{Introduction}
+% This document has been adapted from the instructions
+% for earlier ACL and NAACL proceedings,
+% including 
+% those for ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
+% NAACL 2018 by Margaret Michell and Stephanie Lukin,
+% 2017/2018 (NA)ACL bibtex suggestions from Jason Eisner,
+% ACL 2017 by Dan Gildea and Min-Yen Kan, 
+% NAACL 2017 by Margaret Mitchell, 
+% ACL 2012 by Maggie Li and Michael White, 
+% those from ACL 2010 by Jing-Shing Chang and Philipp Koehn, 
+% those for ACL 2008 by JohannaD. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
+% those for ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
+% those for ACL 2002 by Eugene Charniak and Dekang Lin, 
+% and earlier ACL and EACL formats.
+% Those versions were written by several
+% people, including John Chen, Henry S. Thompson and Donald
+% Walker. Additional elements were taken from the formatting
+% instructions of the {\em International Joint Conference on Artificial
+%   Intelligence} and the \emph{Conference on Computer Vision and
+%   Pattern Recognition}.
 
-The following instructions are directed to authors of papers submitted
-to NAACL-HLT 2019 or accepted for publication in its proceedings. All
-authors are required to adhere to these specifications. Authors are
-required to provide a Portable Document Format (PDF) version of their
-papers. \textbf{The proceedings are designed for printing on A4
-paper.}
+% \section{Introduction}
 
-\section{General Instructions}
+% For example, when a human learns how to jump, they do not forget how to walk.
 
-Manuscripts must be in two-column format.  Exceptions to the
-two-column format include the title, authors' names and complete
-addresses, which must be centered at the top of the first page, and
-any full-width figures or tables (see the guidelines in
-Subsection~\ref{ssec:first}). {\bf Type single-spaced.}  Start all
-pages directly under the top margin. See the guidelines later
-regarding formatting the first page.  The manuscript should be
-printed single-sided and its length
-should not exceed the maximum page limit described in Section~\ref{sec:length}.
-Pages are numbered for  initial submission. However, {\bf do not number the pages in the camera-ready version}.
+% \section{General Instructions}
 
-By uncommenting {\small\verb|\aclfinalcopy|} at the top of this 
- document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.
+% Manuscripts must be in two-column format.  Exceptions to the
+% two-column format include the title, authors' names and complete
+% addresses, which must be centered at the top of the first page, and
+% any full-width figures or tables (see the guidelines in
+% Subsection~\ref{ssec:first}). {\bf Type single-spaced.}  Start all
+% pages directly under the top margin. See the guidelines later
+% regarding formatting the first page.  The manuscript should be
+% printed single-sided and its length
+% should not exceed the maximum page limit described in Section~\ref{sec:length}.
+% Pages are numbered for  initial submission. However, {\bf do not number the pages in the camera-ready version}.
+
+% By uncommenting {\small\verb|\aclfinalcopy|} at the top of this 
+%  document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.
 When you first create your submission on softconf, please fill in your submitted paper ID where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top.
 
-The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.  
-However, you should maintain space for names and addresses so that they will fit in the final (accepted) version.
+% The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.  
+% However, you should maintain space for names and addresses so that they will fit in the final (accepted) version.
 The NAACL-HLT 2019 \LaTeX\ style will create a titlebox space of 2.5in for you when {\small\verb|\aclfinalcopy|} is commented out.
 
-The author list for submissions should include all (and only) individuals who made substantial contributions to the work presented.
+% The author list for submissions should include all (and only) individuals who made substantial contributions to the work presented.
 Each author listed on a submission to NAACL-HLT 2019 will be notified of submissions, revisions and the final decision.
@@
 
-\subsection{The Ruler}
-The NAACL-HLT 2019 style defines a printed ruler which should be presented in the
-version submitted for review.  The ruler is provided in order that
-reviewers may comment on particular lines in the paper without
-circumlocution.  If you are preparing a document without the provided
-style files, please arrange for an equivalent ruler to
-appear on the final output pages.  The presence or absence of the ruler
-should not change the appearance of any other content on the page.  The
-camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment the {\small\verb|\aclfinalcopy|} command in the document preamble.)
+% \subsection{The Ruler}
+% The NAACL-HLT 2019 style defines a printed ruler which should be presented in the
+% version submitted for review.  The ruler is provided in order that
+% reviewers may comment on particular lines in the paper without
+% circumlocution.  If you are preparing a document without the provided
+% style files, please arrange for an equivalent ruler to
+% appear on the final output pages.  The presence or absence of the ruler
+% should not change the appearance of any other content on the page.  The
+% camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment the {\small\verb|\aclfinalcopy|} command in the document preamble.)
 
-Reviewers: note that the ruler measurements do not align well with
-lines in the paper -- this turns out to be very difficult to do well
-when the paper contains many figures and equations, and, when done,
-looks ugly. In most cases one would expect that the approximate
-location will be adequate, although you can also use fractional
-references ({\em e.g.}, the first paragraph on this page ends at mark $108.5$).
+% Reviewers: note that the ruler measurements do not align well with
+% lines in the paper -- this turns out to be very difficult to do well
+% when the paper contains many figures and equations, and, when done,
+% looks ugly. In most cases one would expect that the approximate
+% location will be adequate, although you can also use fractional
+% references ({\em e.g.}, the first paragraph on this page ends at mark $108.5$).
 
-\subsection{Electronically-available resources}
+% \subsection{Electronically-available resources}
 
-NAACL-HLT provides this description in \LaTeX2e{} ({\small\tt naaclhlt2019.tex}) and PDF
-format ({\small\tt naaclhlt2019.pdf}), along with the \LaTeX2e{} style file used to
-format it ({\small\tt naaclhlt2019.sty}) and an ACL bibliography style ({\small\tt acl\_natbib.bst})
-and example bibliography ({\small\tt naaclhlt2019.bib}).
-These files are all available at
-{\small\tt http://naacl2019.org/downloads/ naaclhlt2019-latex.zip}. 
- We
-strongly recommend the use of these style files, which have been
-appropriately tailored for the NAACL-HLT 2019 proceedings.
+% NAACL-HLT provides this description in \LaTeX2e{} ({\small\tt naaclhlt2019.tex}) and PDF
+% format ({\small\tt naaclhlt2019.pdf}), along with the \LaTeX2e{} style file used to
+% format it ({\small\tt naaclhlt2019.sty}) and an ACL bibliography style ({\small\tt acl\_natbib.bst})
+% and example bibliography ({\small\tt naaclhlt2019.bib}).
+% These files are all available at
+% {\small\tt http://naacl2019.org/downloads/ naaclhlt2019-latex.zip}. 
+%  We
+% strongly recommend the use of these style files, which have been
+% appropriately tailored for the NAACL-HLT 2019 proceedings.
 
-\subsection{Format of Electronic Manuscript}
-\label{sect:pdf}
+% \subsection{Format of Electronic Manuscript}
+% \label{sect:pdf}
 
-For the production of the electronic manuscript you must use Adobe's
-Portable Document Format (PDF). PDF files are usually produced from
-\LaTeX\ using the \textit{pdflatex} command. If your version of
-\LaTeX\ produces Postscript files, you can convert these into PDF
-using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
-Adobe Distiller to generate PDF.
+% For the production of the electronic manuscript you must use Adobe's
+% Portable Document Format (PDF). PDF files are usually produced from
+% \LaTeX\ using the \textit{pdflatex} command. If your version of
+% \LaTeX\ produces Postscript files, you can convert these into PDF
+% using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
+% Adobe Distiller to generate PDF.
 
-Please make sure that your PDF file includes all the necessary fonts
-(especially tree diagrams, symbols, and fonts with Asian
-characters). When you print or create the PDF file, there is usually
-an option in your printer setup to include none, all or just
-non-standard fonts.  Please make sure that you select the option of
-including ALL the fonts. \textbf{Before sending it, test your PDF by
-  printing it from a computer different from the one where it was
-  created.} Moreover, some word processors may generate very large PDF
-files, where each page is rendered as an image. Such images may
-reproduce poorly. In this case, try alternative ways to obtain the
-PDF. One way on some systems is to install a driver for a postscript
-printer, send your document to the printer specifying ``Output to a
-file'', then convert the file to PDF.
+% Please make sure that your PDF file includes all the necessary fonts
+% (especially tree diagrams, symbols, and fonts with Asian
+% characters). When you print or create the PDF file, there is usually
+% an option in your printer setup to include none, all or just
+% non-standard fonts.  Please make sure that you select the option of
+% including ALL the fonts. \textbf{Before sending it, test your PDF by
+%   printing it from a computer different from the one where it was
+%   created.} Moreover, some word processors may generate very large PDF
+% files, where each page is rendered as an image. Such images may
+% reproduce poorly. In this case, try alternative ways to obtain the
+% PDF. One way on some systems is to install a driver for a postscript
+% printer, send your document to the printer specifying ``Output to a
+% file'', then convert the file to PDF.
 
-It is of utmost importance to specify the \textbf{A4 format} (21 cm
-x 29.7 cm) when formatting the paper. When working with
-{\tt dvips}, for instance, one should specify {\tt -t a4}.
-Or using the command \verb|\special{papersize=210mm,297mm}| in the latex
-preamble (directly below the \verb|\usepackage| commands). Then using 
-{\tt dvipdf} and/or {\tt pdflatex} which would make it easier for some.
+% It is of utmost importance to specify the \textbf{A4 format} (21 cm
+% x 29.7 cm) when formatting the paper. When working with
+% {\tt dvips}, for instance, one should specify {\tt -t a4}.
+% Or using the command \verb|\special{papersize=210mm,297mm}| in the latex
+% preamble (directly below the \verb|\usepackage| commands). Then using 
+% {\tt dvipdf} and/or {\tt pdflatex} which would make it easier for some.
 
-Print-outs of the PDF file on A4 paper should be identical to the
-hardcopy version. If you cannot meet the above requirements about the
-production of your electronic submission, please contact the
-publication chairs as soon as possible.
+% Print-outs of the PDF file on A4 paper should be identical to the
+% hardcopy version. If you cannot meet the above requirements about the
+% production of your electronic submission, please contact the
+% publication chairs as soon as possible.
 
-\subsection{Layout}
-\label{ssec:layout}
+% \subsection{Layout}
+% \label{ssec:layout}
 
-Format manuscripts two columns to a page, in the manner these
-instructions are formatted. The exact dimensions for a page on A4
-paper are:
+% Format manuscripts two columns to a page, in the manner these
+% instructions are formatted. The exact dimensions for a page on A4
+% paper are:
 
-\begin{itemize}
-\item Left and right margins: 2.5 cm
-\item Top margin: 2.5 cm
-\item Bottom margin: 2.5 cm
-\item Column width: 7.7 cm
-\item Column height: 24.7 cm
-\item Gap between columns: 0.6 cm
-\end{itemize}
+% \begin{itemize}
+% \item Left and right margins: 2.5 cm
+% \item Top margin: 2.5 cm
+% \item Bottom margin: 2.5 cm
+% \item Column width: 7.7 cm
+% \item Column height: 24.7 cm
+% \item Gap between columns: 0.6 cm
+% \end{itemize}
 
-\noindent Papers should not be submitted on any other paper size.
- If you cannot meet the above requirements about the production of 
- your electronic submission, please contact the publication chairs 
- above as soon as possible.
+% \noindent Papers should not be submitted on any other paper size.
+%  If you cannot meet the above requirements about the production of 
+%  your electronic submission, please contact the publication chairs 
+%  above as soon as possible.
 
-\subsection{Fonts}
+% \subsection{Fonts}
 
-For reasons of uniformity, Adobe's {\bf Times Roman} font should be
-used. In \LaTeX2e{} this is accomplished by putting
+% For reasons of uniformity, Adobe's {\bf Times Roman} font should be
+% used. In \LaTeX2e{} this is accomplished by putting
 
-\begin{quote}
-\begin{verbatim}
-\usepackage{times}
-\usepackage{latexsym}
-\end{verbatim}
-\end{quote}
-in the preamble. If Times Roman is unavailable, use {\bf Computer
-  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
-  10\% less dense than Adobe's Times Roman font.
+% \begin{quote}
+% \begin{verbatim}
+% \usepackage{times}
+% \usepackage{latexsym}
+% \end{verbatim}
+% \end{quote}
+% in the preamble. If Times Roman is unavailable, use {\bf Computer
+%   Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
+%   10\% less dense than Adobe's Times Roman font.
 
-\begin{table}[t!]
-\begin{center}
-\begin{tabular}{|l|rl|}
-\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
-paper title & 15 pt & bold \\
-author names & 12 pt & bold \\
-author affiliation & 12 pt & \\
-the word ``Abstract'' & 12 pt & bold \\
-section titles & 12 pt & bold \\
-document text & 11 pt  &\\
-captions & 10 pt & \\
-abstract text & 10 pt & \\
-bibliography & 10 pt & \\
-footnotes & 9 pt & \\
-\hline
-\end{tabular}
-\end{center}
-\caption{\label{font-table} Font guide. }
-\end{table}
+% \begin{table}[t!]
+% \begin{center}
+% \begin{tabular}{|l|rl|}
+% \hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
+% paper title & 15 pt & bold \\
+% author names & 12 pt & bold \\
+% author affiliation & 12 pt & \\
+% the word ``Abstract'' & 12 pt & bold \\
+% section titles & 12 pt & bold \\
+% document text & 11 pt  &\\
+% captions & 10 pt & \\
+% abstract text & 10 pt & \\
+% bibliography & 10 pt & \\
+% footnotes & 9 pt & \\
+% \hline
+% \end{tabular}
+% \end{center}
+% \caption{\label{font-table} Font guide. }
+% \end{table}
 
-\subsection{The First Page}
-\label{ssec:first}
+% \subsection{The First Page}
+% \label{ssec:first}
 
-Center the title, author's name(s) and affiliation(s) across both
-columns. Do not use footnotes for affiliations. Do not include the
-paper ID number assigned during the submission process. Use the
-two-column format only when you begin the abstract.
+% Center the title, author's name(s) and affiliation(s) across both
+% columns. Do not use footnotes for affiliations. Do not include the
+% paper ID number assigned during the submission process. Use the
+% two-column format only when you begin the abstract.
 
-{\bf Title}: Place the title centered at the top of the first page, in
-a 15-point bold font. (For a complete guide to font sizes and styles,
-see Table~\ref{font-table}) Long titles should be typed on two lines
-without a blank line intervening. Approximately, put the title at 2.5
-cm from the top of the page, followed by a blank line, then the
-author's names(s), and the affiliation on the following line. Do not
-use only initials for given names (middle initials are allowed). Do
-not format surnames in all capitals ({\em e.g.}, use ``Mitchell'' not
-``MITCHELL'').  Do not format title and section headings in all
-capitals as well except for proper names (such as ``BLEU'') that are
-conventionally in all capitals.  The affiliation should contain the
-author's complete address, and if possible, an electronic mail
-address. Start the body of the first page 7.5 cm from the top of the
-page.
+% {\bf Title}: Place the title centered at the top of the first page, in
+% a 15-point bold font. (For a complete guide to font sizes and styles,
+% see Table~\ref{font-table}) Long titles should be typed on two lines
+% without a blank line intervening. Approximately, put the title at 2.5
+% cm from the top of the page, followed by a blank line, then the
+% author's names(s), and the affiliation on the following line. Do not
+% use only initials for given names (middle initials are allowed). Do
+% not format surnames in all capitals ({\em e.g.}, use ``Mitchell'' not
+% ``MITCHELL'').  Do not format title and section headings in all
+% capitals as well except for proper names (such as ``BLEU'') that are
+% conventionally in all capitals.  The affiliation should contain the
+% author's complete address, and if possible, an electronic mail
+% address. Start the body of the first page 7.5 cm from the top of the
+% page.
 
-The title, author names and addresses should be completely identical
-to those entered to the electronical paper submission website in order
-to maintain the consistency of author information among all
-publications of the conference. If they are different, the publication
-chairs may resolve the difference without consulting with you; so it
-is in your own interest to double-check that the information is
-consistent.
+% The title, author names and addresses should be completely identical
+% to those entered to the electronical paper submission website in order
+% to maintain the consistency of author information among all
+% publications of the conference. If they are different, the publication
+% chairs may resolve the difference without consulting with you; so it
+% is in your own interest to double-check that the information is
+% consistent.
 
-{\bf Abstract}: Type the abstract at the beginning of the first
-column. The width of the abstract text should be smaller than the
-width of the columns for the text in the body of the paper by about
-0.6 cm on each side. Center the word {\bf Abstract} in a 12 point bold
-font above the body of the abstract. The abstract should be a concise
-summary of the general thesis and conclusions of the paper. It should
-be no longer than 200 words. The abstract text should be in 10 point font.
+% {\bf Abstract}: Type the abstract at the beginning of the first
+% column. The width of the abstract text should be smaller than the
+% width of the columns for the text in the body of the paper by about
+% 0.6 cm on each side. Center the word {\bf Abstract} in a 12 point bold
+% font above the body of the abstract. The abstract should be a concise
+% summary of the general thesis and conclusions of the paper. It should
+% be no longer than 200 words. The abstract text should be in 10 point font.
 
-{\bf Text}: Begin typing the main body of the text immediately after
-the abstract, observing the two-column format as shown in the present document. Do not include page numbers.
+% {\bf Text}: Begin typing the main body of the text immediately after
+% the abstract, observing the two-column format as shown in the present document. Do not include page numbers.
 
-{\bf Indent}: Indent when starting a new paragraph, about 0.4 cm. Use 11 points for text and subsection headings, 12 points for section headings and 15 points for the title.
+% {\bf Indent}: Indent when starting a new paragraph, about 0.4 cm. Use 11 points for text and subsection headings, 12 points for section headings and 15 points for the title.
 
-\begin{table}
-\centering
-\small
-\begin{tabular}{cc}
-\begin{tabular}{|l|l|}
-\hline
-{\bf Command} & {\bf Output}\\\hline
-\verb|{\"a}| & {\"a} \\
-\verb|{\^e}| & {\^e} \\
-\verb|{\`i}| & {\`i} \\ 
-\verb|{\.I}| & {\.I} \\ 
-\verb|{\o}| & {\o} \\
-\verb|{\'u}| & {\'u}  \\ 
-\verb|{\aa}| & {\aa}  \\\hline
-\end{tabular} & 
-\begin{tabular}{|l|l|}
-\hline
-{\bf Command} & {\bf  Output}\\\hline
-\verb|{\c c}| & {\c c} \\ 
-\verb|{\u g}| & {\u g} \\ 
-\verb|{\l}| & {\l} \\ 
-\verb|{\~n}| & {\~n} \\ 
-\verb|{\H o}| & {\H o} \\ 
-\verb|{\v r}| & {\v r} \\ 
-\verb|{\ss}| & {\ss} \\\hline
-\end{tabular}
-\end{tabular}
-\caption{Example commands for accented characters, to be used in, {\em e.g.}, \BibTeX\ names.}\label{tab:accents}
-\end{table}
+% \begin{table}
+% \centering
+% \small
+% \begin{tabular}{cc}
+% \begin{tabular}{|l|l|}
+% \hline
+% {\bf Command} & {\bf Output}\\\hline
+% \verb|{\"a}| & {\"a} \\
+% \verb|{\^e}| & {\^e} \\
+% \verb|{\`i}| & {\`i} \\ 
+% \verb|{\.I}| & {\.I} \\ 
+% \verb|{\o}| & {\o} \\
+% \verb|{\'u}| & {\'u}  \\ 
+% \verb|{\aa}| & {\aa}  \\\hline
+% \end{tabular} & 
+% \begin{tabular}{|l|l|}
+% \hline
+% {\bf Command} & {\bf  Output}\\\hline
+% \verb|{\c c}| & {\c c} \\ 
+% \verb|{\u g}| & {\u g} \\ 
+% \verb|{\l}| & {\l} \\ 
+% \verb|{\~n}| & {\~n} \\ 
+% \verb|{\H o}| & {\H o} \\ 
+% \verb|{\v r}| & {\v r} \\ 
+% \verb|{\ss}| & {\ss} \\\hline
+% \end{tabular}
+% \end{tabular}
+% \caption{Example commands for accented characters, to be used in, {\em e.g.}, \BibTeX\ names.}\label{tab:accents}
+% \end{table}
 
-\subsection{Sections}
+% \subsection{Sections}
 
-{\bf Headings}: Type and label section and subsection headings in the
-style shown on the present document.  Use numbered sections (Arabic
-numerals) in order to facilitate cross references. Number subsections
-with the section number and the subsection number separated by a dot,
-in Arabic numerals.
-Do not number subsubsections.
+% {\bf Headings}: Type and label section and subsection headings in the
+% style shown on the present document.  Use numbered sections (Arabic
+% numerals) in order to facilitate cross references. Number subsections
+% with the section number and the subsection number separated by a dot,
+% in Arabic numerals.
+% Do not number subsubsections.
 
-\begin{table*}[t!]
-\centering
-\begin{tabular}{lll}
-  output & natbib & previous ACL style files\\
-  \hline
-  \citep{Gusfield:97} & \verb|\citep| & \verb|\cite| \\
-  \citet{Gusfield:97} & \verb|\citet| & \verb|\newcite| \\
-  \citeyearpar{Gusfield:97} & \verb|\citeyearpar| & \verb|\shortcite| \\
-\end{tabular}
-\caption{Citation commands supported by the style file.
-  The citation style is based on the natbib package and
-  supports all natbib citation commands.
-  It also supports commands defined in previous ACL style files
-  for compatibility.
-  }
-\end{table*}
+% \begin{table*}[t!]
+% \centering
+% \begin{tabular}{lll}
+%   output & natbib & previous ACL style files\\
+%   \hline
+%   \citep{Gusfield:97} & \verb|\citep| & \verb|\cite| \\
+%   \citet{Gusfield:97} & \verb|\citet| & \verb|\newcite| \\
+%   \citeyearpar{Gusfield:97} & \verb|\citeyearpar| & \verb|\shortcite| \\
+% \end{tabular}
+% \caption{Citation commands supported by the style file.
+%   The citation style is based on the natbib package and
+%   supports all natbib citation commands.
+%   It also supports commands defined in previous ACL style files
+%   for compatibility.
+%   }
+% \end{table*}
 
-{\bf Citations}: Citations within the text appear in parentheses
-as~\cite{Gusfield:97} or, if the author's name appears in the text
-itself, as Gusfield~\shortcite{Gusfield:97}.
-Using the provided \LaTeX\ style, the former is accomplished using
-{\small\verb|\cite|} and the latter with {\small\verb|\shortcite|} or {\small\verb|\newcite|}.
+% {\bf Citations}: Citations within the text appear in parentheses
+% as~\cite{Gusfield:97} or, if the author's name appears in the text
+% itself, as Gusfield~\shortcite{Gusfield:97}.
+% Using the provided \LaTeX\ style, the former is accomplished using
+% {\small\verb|\cite|} and the latter with {\small\verb|\shortcite|} or {\small\verb|\newcite|}.
 Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}; this is accomplished with the provided style using commas within the {\small\verb|\cite|} command, {\em e.g.}, {\small\verb|\cite{Gusfield:97,Aho:72}|}.
 Append lowercase letters to the year in cases of ambiguities.
- Treat double authors as
-in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two
-authors are involved. Collapse multiple citations as
-in~\cite{Gusfield:97,Aho:72}. Also refrain from using full citations
-as sentence constituents.
+%  Treat double authors as
+% in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two
+% authors are involved. Collapse multiple citations as
+% in~\cite{Gusfield:97,Aho:72}. Also refrain from using full citations
+% as sentence constituents.
 
-We suggest that instead of
-\begin{quote}
-  ``\cite{Gusfield:97} showed that ...''
-\end{quote}
-you use
-\begin{quote}
-``Gusfield \shortcite{Gusfield:97}   showed that ...''
-\end{quote}
+% We suggest that instead of
+% \begin{quote}
+%   ``\cite{Gusfield:97} showed that ...''
+% \end{quote}
+% you use
+% \begin{quote}
+% ``Gusfield \shortcite{Gusfield:97}   showed that ...''
+% \end{quote}
 
-If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
-can use the command \verb|\citet| (cite in text)
-to get ``author (year)'' citations.
+% If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
+% can use the command \verb|\citet| (cite in text)
+% to get ``author (year)'' citations.
 
-If the Bib\TeX{} file contains DOI fields, the paper
-title in the references section will appear as a hyperlink
-to the DOI, using the hyperref \LaTeX{} package.
-To disable the hyperref package, load the style file
-with the \verb|nohyperref| option: \\{\small
-\verb|\usepackage[nohyperref]{naaclhlt2019}|}
+% If the Bib\TeX{} file contains DOI fields, the paper
+% title in the references section will appear as a hyperlink
+% to the DOI, using the hyperref \LaTeX{} package.
+% To disable the hyperref package, load the style file
+% with the \verb|nohyperref| option: \\{\small
+% \verb|\usepackage[nohyperref]{naaclhlt2019}|}
 
-\textbf{Digital Object Identifiers}:  As part of our work to make ACL
-materials more widely used and cited outside of our discipline, ACL
-has registered as a CrossRef member, as a registrant of Digital Object
-Identifiers (DOIs), the standard for registering permanent URNs for
-referencing scholarly materials.  As of 2017, we are requiring all
-camera-ready references to contain the appropriate DOIs (or as a
-second resort, the hyperlinked ACL Anthology Identifier) to all cited
-works.  Thus, please ensure that you use Bib\TeX\ records that contain
-DOI or URLs for any of the ACL materials that you reference.
-Appropriate records should be found for most materials in the current
-ACL Anthology at \url{http://aclanthology.info/}.
+% \textbf{Digital Object Identifiers}:  As part of our work to make ACL
+% materials more widely used and cited outside of our discipline, ACL
+% has registered as a CrossRef member, as a registrant of Digital Object
+% Identifiers (DOIs), the standard for registering permanent URNs for
+% referencing scholarly materials.  As of 2017, we are requiring all
+% camera-ready references to contain the appropriate DOIs (or as a
+% second resort, the hyperlinked ACL Anthology Identifier) to all cited
+% works.  Thus, please ensure that you use Bib\TeX\ records that contain
+% DOI or URLs for any of the ACL materials that you reference.
+% Appropriate records should be found for most materials in the current
+% ACL Anthology at \url{http://aclanthology.info/}.
 
-As examples, we cite \cite{P16-1001} to show you how papers with a DOI
-will appear in the bibliography.  We cite \cite{C14-1001} to show how
-papers without a DOI but with an ACL Anthology Identifier will appear
-in the bibliography.
+% As examples, we cite \cite{P16-1001} to show you how papers with a DOI
+% will appear in the bibliography.  We cite \cite{C14-1001} to show how
+% papers without a DOI but with an ACL Anthology Identifier will appear
+% in the bibliography.
 
-As reviewing will be double-blind, the submitted version of the papers
-should not include the authors' names and affiliations. Furthermore,
-self-references that reveal the author's identity, {\em e.g.},
-\begin{quote}
-``We previously showed \cite{Gusfield:97} ...''  
-\end{quote}
-should be avoided. Instead, use citations such as 
-\begin{quote}
-``\citeauthor{Gusfield:97} \shortcite{Gusfield:97}
-previously showed ... ''
-\end{quote}
+% As reviewing will be double-blind, the submitted version of the papers
+% should not include the authors' names and affiliations. Furthermore,
+% self-references that reveal the author's identity, {\em e.g.},
+% \begin{quote}
+% ``We previously showed \cite{Gusfield:97} ...''  
+% \end{quote}
+% should be avoided. Instead, use citations such as 
+% \begin{quote}
+% ``\citeauthor{Gusfield:97} \shortcite{Gusfield:97}
+% previously showed ... ''
+% \end{quote}
 
-Any preliminary non-archival versions of submitted papers should be listed in the submission form but not in the review version of the paper.
+% Any preliminary non-archival versions of submitted papers should be listed in the submission form but not in the review version of the paper.
 NAACL-HLT 2019 reviewers are generally aware that authors may present preliminary versions of their work in other venues, but will not be provided the list of previous presentations from the submission form.
 
-\textbf{Please do not use anonymous citations} and do not include
- when submitting your papers. Papers that do not
-conform to these requirements may be rejected without review.
+% \textbf{Please do not use anonymous citations} and do not include
+%  when submitting your papers. Papers that do not
+% conform to these requirements may be rejected without review.
 
-\textbf{References}: Gather the full set of references together under
-the heading {\bf References}; place the section before any Appendices. 
-Arrange the references alphabetically
-by first author, rather than by order of occurrence in the text.
-By using a .bib file, as in this template, this will be automatically 
-handled for you. See the \verb|\bibliography| commands near the end for more.
+% \textbf{References}: Gather the full set of references together under
+% the heading {\bf References}; place the section before any Appendices. 
+% Arrange the references alphabetically
+% by first author, rather than by order of occurrence in the text.
+% By using a .bib file, as in this template, this will be automatically 
+% handled for you. See the \verb|\bibliography| commands near the end for more.
 
-Provide as complete a citation as possible, using a consistent format,
-such as the one for {\em Computational Linguistics\/} or the one in the 
-{\em Publication Manual of the American 
-Psychological Association\/}~\cite{APA:83}. Use of full names for
-authors rather than initials is preferred. A list of abbreviations
-for common computer science journals can be found in the ACM 
-{\em Computing Reviews\/}~\cite{ACM:83}.
+% Provide as complete a citation as possible, using a consistent format,
+% such as the one for {\em Computational Linguistics\/} or the one in the 
+% {\em Publication Manual of the American 
+% Psychological Association\/}~\cite{APA:83}. Use of full names for
+% authors rather than initials is preferred. A list of abbreviations
+% for common computer science journals can be found in the ACM 
+% {\em Computing Reviews\/}~\cite{ACM:83}.
 
-The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
-American Psychological Association format, allowing regular citations, 
-short citations and multiple citations as described above.
+% The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
+% American Psychological Association format, allowing regular citations, 
+% short citations and multiple citations as described above.
 
-\begin{itemize}
-\item Example citing an arxiv paper: \cite{rasooli-tetrault-2015}. 
-\item Example article in journal citation: \cite{Ando2005}.
-\item Example article in proceedings, with location: \cite{borsch2011}.
-\item Example article in proceedings, without location: \cite{andrew2007scalable}.
-\end{itemize}
-See corresponding .bib file for further details.
+% \begin{itemize}
+% \item Example citing an arxiv paper: \cite{rasooli-tetrault-2015}. 
+% \item Example article in journal citation: \cite{Ando2005}.
+% \item Example article in proceedings, with location: \cite{borsch2011}.
+% \item Example article in proceedings, without location: \cite{andrew2007scalable}.
+% \end{itemize}
+% See corresponding .bib file for further details.
 
-Submissions should accurately reference prior and related work, including code and data.
+% Submissions should accurately reference prior and related work, including code and data.
 If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced.
@@
 
-{\bf Appendices}: Appendices, if any, directly follow the text and the
-references (but see above).  Letter them in sequence and provide an
-informative title: {\bf Appendix A. Title of Appendix}.
+% {\bf Appendices}: Appendices, if any, directly follow the text and the
+% references (but see above).  Letter them in sequence and provide an
+% informative title: {\bf Appendix A. Title of Appendix}.
 
-\subsection{Footnotes}
+% \subsection{Footnotes}
 
-{\bf Footnotes}: Put footnotes at the bottom of the page and use 9
-point font. They may be numbered or referred to by asterisks or other
-symbols.\footnote{This is how a footnote should appear.} Footnotes
-should be separated from the text by a line.\footnote{Note the line
-separating the footnotes from the text.}
+% {\bf Footnotes}: Put footnotes at the bottom of the page and use 9
+% point font. They may be numbered or referred to by asterisks or other
+% symbols.\footnote{This is how a footnote should appear.} Footnotes
+% should be separated from the text by a line.\footnote{Note the line
+% separating the footnotes from the text.}
 
-\subsection{Graphics}
+% \subsection{Graphics}
 
-{\bf Illustrations}: Place figures, tables, and photographs in the
-paper near where they are first discussed, rather than at the end, if
-possible.  Wide illustrations may run across both columns.  Color
-illustrations are discouraged, unless you have verified that  
-they will be understandable when printed in black ink.
+% {\bf Illustrations}: Place figures, tables, and photographs in the
+% paper near where they are first discussed, rather than at the end, if
+% possible.  Wide illustrations may run across both columns.  Color
+% illustrations are discouraged, unless you have verified that  
+% they will be understandable when printed in black ink.
 
-{\bf Captions}: Provide a caption for every illustration; number each one
-sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
-Caption of the Table.''  Type the captions of the figures and 
-tables below the body, using 10 point text.
+% {\bf Captions}: Provide a caption for every illustration; number each one
+% sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
+% Caption of the Table.''  Type the captions of the figures and 
+% tables below the body, using 10 point text.
 Captions should be placed below illustrations.
@@
 
-\subsection{Accessibility}
-\label{ssec:accessibility}
+% \subsection{Accessibility}
+% \label{ssec:accessibility}
 
-In an effort to accommodate people who are color-blind (as well as those printing
-to paper), grayscale readability for all accepted papers will be
-encouraged.  Color is not forbidden, but authors should ensure that
-tables and figures do not rely solely on color to convey critical
-distinctions. A simple criterion: All curves and points in your figures should be clearly distinguishable without color.
+% In an effort to accommodate people who are color-blind (as well as those printing
+% to paper), grayscale readability for all accepted papers will be
+% encouraged.  Color is not forbidden, but authors should ensure that
+% tables and figures do not rely solely on color to convey critical
+% distinctions. A simple criterion: All curves and points in your figures should be clearly distinguishable without color.
 
-% Min: no longer used as of ACL 2018, following ACL exec's decision to
-% remove this extra workflow that was not executed much.
-% BEGIN: remove
-%% \section{XML conversion and supported \LaTeX\ packages}
+% % Min: no longer used as of ACL 2018, following ACL exec's decision to
+% % remove this extra workflow that was not executed much.
+% % BEGIN: remove
+% %% \section{XML conversion and supported \LaTeX\ packages}
 
-%% Following ACL 2014 we will also we will attempt to automatically convert 
-%% your \LaTeX\ source files to publish papers in machine-readable 
-%% XML with semantic markup in the ACL Anthology, in addition to the 
-%% traditional PDF format.  This will allow us to create, over the next 
-%% few years, a growing corpus of scientific text for our own future research, 
-%% and picks up on recent initiatives on converting ACL papers from earlier 
-%% years to XML.
+% %% Following ACL 2014 we will also we will attempt to automatically convert 
+% %% your \LaTeX\ source files to publish papers in machine-readable 
+% %% XML with semantic markup in the ACL Anthology, in addition to the 
+% %% traditional PDF format.  This will allow us to create, over the next 
+% %% few years, a growing corpus of scientific text for our own future research, 
+% %% and picks up on recent initiatives on converting ACL papers from earlier 
+% %% years to XML.
 
-%% We encourage you to submit a ZIP file of your \LaTeX\ sources along
-%% with the camera-ready version of your paper. We will then convert them
-%% to XML automatically, using the LaTeXML tool
-%% (\url{http://dlmf.nist.gov/LaTeXML}). LaTeXML has \emph{bindings} for
-%% a number of \LaTeX\ packages, including the ACL 2018 stylefile. These
-%% bindings allow LaTeXML to render the commands from these packages
-%% correctly in XML. For best results, we encourage you to use the
-%% packages that are officially supported by LaTeXML, listed at
-%% \url{http://dlmf.nist.gov/LaTeXML/manual/included.bindings}
-% END: remove
+% %% We encourage you to submit a ZIP file of your \LaTeX\ sources along
+% %% with the camera-ready version of your paper. We will then convert them
+% %% to XML automatically, using the LaTeXML tool
+% %% (\url{http://dlmf.nist.gov/LaTeXML}). LaTeXML has \emph{bindings} for
+% %% a number of \LaTeX\ packages, including the ACL 2018 stylefile. These
+% %% bindings allow LaTeXML to render the commands from these packages
+% %% correctly in XML. For best results, we encourage you to use the
+% %% packages that are officially supported by LaTeXML, listed at
+% %% \url{http://dlmf.nist.gov/LaTeXML/manual/included.bindings}
+% % END: remove
 
-\section{Translation of non-English Terms}
+% \section{Translation of non-English Terms}
 
-It is also advised to supplement non-English characters and terms
-with appropriate transliterations and/or translations
-since not all readers understand all such characters and terms.
-Inline transliteration or translation can be represented in
-the order of: original-form transliteration ``translation''.
+% It is also advised to supplement non-English characters and terms
+% with appropriate transliterations and/or translations
+% since not all readers understand all such characters and terms.
+% Inline transliteration or translation can be represented in
+% the order of: original-form transliteration ``translation''.
 
-\section{Length of Submission}
-\label{sec:length}
+% \section{Length of Submission}
+% \label{sec:length}
 
-The NAACL-HLT 2019 main conference accepts submissions of long papers and
-short papers.
- Long papers may consist of up to eight (8) pages of
-content plus unlimited pages for references. Upon acceptance, final
-versions of long papers will be given one additional page -- up to nine (9)
-pages of content plus unlimited pages for references -- so that reviewers' comments
-can be taken into account. Short papers may consist of up to four (4)
-pages of content, plus unlimited pages for references. Upon
-acceptance, short papers will be given five (5) pages in the
-proceedings and unlimited pages for references. 
-For both long and short papers, all illustrations and tables that are part
-of the main text must be accommodated within these page limits, observing
-the formatting instructions given in the present document. Papers that do not conform to the specified length and formatting requirements are subject to be rejected without review.
+% The NAACL-HLT 2019 main conference accepts submissions of long papers and
+% short papers.
+%  Long papers may consist of up to eight (8) pages of
+% content plus unlimited pages for references. Upon acceptance, final
+% versions of long papers will be given one additional page -- up to nine (9)
+% pages of content plus unlimited pages for references -- so that reviewers' comments
+% can be taken into account. Short papers may consist of up to four (4)
+% pages of content, plus unlimited pages for references. Upon
+% acceptance, short papers will be given five (5) pages in the
+% proceedings and unlimited pages for references. 
+% For both long and short papers, all illustrations and tables that are part
+% of the main text must be accommodated within these page limits, observing
+% the formatting instructions given in the present document. Papers that do not conform to the specified length and formatting requirements are subject to be rejected without review.
 
-NAACL-HLT 2019 does encourage the submission of additional material that is relevant to the reviewers but not an integral part of the paper.
+% NAACL-HLT 2019 does encourage the submission of additional material that is relevant to the reviewers but not an integral part of the paper.
 There are two such types of material: appendices, which can be read, and non-readable supplementary materials, often data or code.
@@
 
-Workshop chairs may have different rules for allowed length and
-whether supplemental material is welcome. As always, the respective
-call for papers is the authoritative source.
+% Workshop chairs may have different rules for allowed length and
+% whether supplemental material is welcome. As always, the respective
+% call for papers is the authoritative source.
 
-\section*{Acknowledgments}
+% \section*{Acknowledgments}
 
-The acknowledgments should go immediately before the references.  Do
-not number the acknowledgments section. Do not include this section
-when submitting your paper for review. \\
+% The acknowledgments should go immediately before the references.  Do
+% not number the acknowledgments section. Do not include this section
+% when submitting your paper for review. \\
 
-\noindent {\bf Preparing References:} \\
-Include your own bib file like this:
-\verb|\bibliographystyle{acl_natbib}|
-\verb|\bibliography{naaclhlt2019}|
+% \noindent {\bf Preparing References:} \\
+% Include your own bib file like this:
+% \verb|\bibliographystyle{acl_natbib}|
+% \verb|\bibliography{naaclhlt2019}|
 
-where \verb|naaclhlt2019| corresponds to a naaclhlt2019.bib file.
-\bibliography{naaclhlt2019}
-\bibliographystyle{acl_natbib}
+% where \verb|naaclhlt2019| corresponds to a naaclhlt2019.bib file.
+% \bibliography{naaclhlt2019}
+% \bibliographystyle{acl_natbib}
 
-\appendix
+% \appendix
 
-\section{Appendices}
-\label{sec:appendix}
-Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
-Appendices should be {\bf uploaded as supplementary material} when submitting the paper for review. Upon acceptance, the appendices come after the references, as shown here. Use
-\verb|\appendix| before any appendix section to switch the section
-numbering over to letters.
+% \section{Appendices}
+% \label{sec:appendix}
+% Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
+% Appendices should be {\bf uploaded as supplementary material} when submitting the paper for review. Upon acceptance, the appendices come after the references, as shown here. Use
+% \verb|\appendix| before any appendix section to switch the section
+% numbering over to letters.
 
-\section{Supplemental Material}
-\label{sec:supplemental}
-Submissions may include non-readable supplementary material used in the work and described in the paper.
+% \section{Supplemental Material}
+% \label{sec:supplemental}
+% Submissions may include non-readable supplementary material used in the work and described in the paper.
 Any accompanying software and/or data should include licenses and documentation of research review as appropriate.
@@
 
-Nonetheless, supplementary material should be supplementary (rather
-than central) to the paper. {\bf Submissions that misuse the supplementary 
-material may be rejected without review.}
-Supplementary material may include explanations or details
-of proofs or derivations that do not fit into the paper, lists of
-features or feature templates, sample inputs and outputs for a system,
-pseudo-code or source code, and data. (Source code and data should
-be separate uploads, rather than part of the paper).
+% Nonetheless, supplementary material should be supplementary (rather
+% than central) to the paper. {\bf Submissions that misuse the supplementary 
+% material may be rejected without review.}
+% Supplementary material may include explanations or details
+% of proofs or derivations that do not fit into the paper, lists of
+% features or feature templates, sample inputs and outputs for a system,
+% pseudo-code or source code, and data. (Source code and data should
+% be separate uploads, rather than part of the paper).
 
-The paper should not rely on the supplementary material: while the paper
-may refer to and cite the supplementary material and the supplementary material will be available to the
-reviewers, they will not be asked to review the
-supplementary material.
+% The paper should not rely on the supplementary material: while the paper
+% may refer to and cite the supplementary material and the supplementary material will be available to the
+% reviewers, they will not be asked to review the
+% supplementary material.
 

### 2020-04-22 MAS/main.py

@@ -146,13 +146,13 @@ def train(args, train_dataset, task, all_tasks, model, task_num, tokenizer, accu
 
     logs = {}
 
-    # results = evaluate(args, model, task, tokenizer, accuracy_matrix, task_num, task_num, "Current Task")
+    results = evaluate(args, model, task, tokenizer, accuracy_matrix, task_num, task_num, "Current Task")
 
     # for key, value in results.items():
     #	eval_key = "eval_{}".format(key)
     #	logs[eval_key] = value
 
-    # print(results)
+    print(results)
 
     loss_scalar = (tr_loss - logging_loss) / args.logging_steps
     # learning_rate_scalar = scheduler.get_lr()[0]

### 2020-04-22 arguments.py
Bug fix in EWC

@@ -56,6 +56,10 @@ def parse_args():
                         action="store_true",
                         default=False
                         )
+    parser.add_argument("--lamda",
+                        default=1000,
+                        type=float
+                        )
 
     args = parser.parse_args()
     with open(args.task_params) as file:

### 2020-04-22 main.py

@@ -70,16 +70,18 @@ def save_model(args, task_num, model):
 
 def compute_ewc_loss(args, lamda, task_num, task, model, consolidate_fisher, consolidate_mean):
     # EWC Loss is computed only on BERT parameters (not on task specific parameters)
-    bert_paramters = model.state_dict().copy()
-    del bert_paramters["classifier.weight"]
-    del bert_paramters['classifier.bias']
+    # bert_paramters = model.state_dict()
+    # del bert_paramters["classifier.weight"]
+    # del bert_paramters['classifier.bias']
 
-    loss_ewc = 0
-    for name, params in bert_paramters.items():
-        mean = Variable(consolidate_mean[task][name])
-        fisher = Variable(consolidate_fisher[task][name])
-        loss_ewc_layer = fisher * (params - mean) ** 2
-        loss_ewc += loss_ewc_layer.sum()
+    loss_ewc = torch.tensor(0.0, requires_grad=True).to(args.device)
+    for name, params in model.named_parameters():
+        if not (name == "classifier.weight" or name == "classifier.bias"):
+            # print(name)
+            mean = consolidate_mean[task][name]
+            fisher = consolidate_fisher[task][name]
+            loss_ewc_layer = fisher * (params - mean) ** 2
+            loss_ewc += loss_ewc_layer.sum()
 
     return (lamda / 2) * loss_ewc
 
@@ -94,10 +96,10 @@ def estimate_fisher_mean(args, train_dataset, model, task, fisher_consolidate, m
     fisher_consolidate[task] = {}
 
     for n, p in model.named_parameters():
-        mean_consolidate[task][n] = Variable(p.data.to(args.device))
+        mean_consolidate[task][n] = p.data.to(args.device)
 
     for n, p in model.named_parameters():
-        fisher_consolidate[task][n] = Variable(torch.zeros(p.size()).to(args.device))
+        fisher_consolidate[task][n] = torch.zeros(p.size()).to(args.device)
 
     model.eval()
     # new_model = copy.deepcopy(model).cpu()
@@ -113,8 +115,8 @@ def estimate_fisher_mean(args, train_dataset, model, task, fisher_consolidate, m
         loss = outputs[0]
         loss.backward()
         for n, p in model.named_parameters():
-            fisher_consolidate[task][n].data += p.grad.data ** 2 / len(train_dataset)
-    fisher_consolidate[task] = {n: p for n, p in fisher_consolidate[task].items()}
[…]

### 2020-04-22 utils.py

@@ -18,7 +18,7 @@ def convert_dict(config, args):
 				"output_dir": args.output_dir,
 				"data_dir": args.data_dir,
 				"max_seq_length": args.max_seq_length,
-				"reg_lambda": args.reg_lambda,
-				"init_lr": args.init_lr
+				"ewc": args.ewc,
+				"lamda": args.lamda
 				})
 	return out

### 2020-04-22 paper/paper.tex
modified:   paper/paper.tex
Updates from Overleaf
paper push

@@
 \usepackage{times}
-\usepackage{latexsym}
+\usepackage{latexsym, amsmath}
 
@@
 
-%\aclfinalcopy % Uncomment this line for the final submission
+\aclfinalcopy % Uncomment this line for the final submission
 %\def\aclpaperid{***} %  Enter the acl Paper ID here
@@
 
+%%%%%%%%%%%%%%%%% GUIDELINES %%%%%%%%%%%%%%%
+% The partial draft in a single document with three pages of content (not counting references, appendix, and contribution statement).
+This should essentially be a near-final draft of your paper (in ACL 2020 paper style) with the results, analysis, and conclusion sections missing.
+It should contain a link to your public GitHub repo, which should show evidence that you have implemented everything you’ll need in order to complete your project.
+
+% Introduction/overall idea (4):
+% Clear overall motivation for project (2)
+% Clear description and motivation for any novel techniques, including baseline results (2)
+
+% Background (3):
+% No major omissions from the literature review (1)
+% 10+ papers cited (1)
+% 5+ relevant papers discussed in detail, with explanations of how they relate to your project (1)
+
+% Overall writing (2):
+% Reasonably close fit to ACL style (1)
+% Readable prose (1)
+% Collaboration statement (0, -1 for groups that leave it out) [We reserve the right to redistribute points unevenly between team members in case of very uneven contributions.]
+
 \newcommand\BibTeX{B{\sc ib}\TeX}
+\usepackage[ruled,vlined]{algorithm2e}
+\title{Continual NLU: Enabling language models to learn downstream tasks in an online fashion}
 
-\title{Life-long NLU: Continual Learning of Downstream Natural Language Tasks}
-
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\}
-
+\author{{Mohith Damarapati*, Govind Mittal*, Chandra Prakash Konkimalla*, Aakriti Gupta}\\
+  {\tt \{md4289, gm2724, cpk290, ag6817\}@nyu.edu}}
 \date{}
-
 \begin{document}
@@
   Qualified general intelligence has the ability of learning new tasks without immediately becoming worse at an older one.
-With this statement at the core of this paper, we explore various techniques to prevent forgetting in a state-of-the-art language model.
-These techniques range involve Elastic Weight Consolidation, Memory aware synapses and semantic intelligence \cite{french1999catastrophic}
+With this statement at the core of this paper, we explore various techniques to prevent catastrophic forgetting (CF) in a state-of-the-art language model.
+The paper explores three neuroscience inspired regularization techniques to mitigate CF, \textit{viz.}, Elastic Weight Consolidation, Memory Aware Synapses and Synaptic Intelligence on pre-trained BERT model.
+Two evaluation metrics -- backward and forward transfer, are used to evaluate the techniques.
+The paper aims to reduce the negative backward transfer for previous tasks and boost positive forward transfer for future tasks.
+As per our knowledge, this is the first work attempting to enable language models to learn downstream tasks in an online fashion and evaluating them based on the metrics mentioned above
 \end{abstract}
 
+% \section{credits
+
+\section{Introduction}
+\label{sec:intro}
+
+Natural cognitive systems gradually forget previously learned information unlike the CF observed in current connectionist approaches \cite{french1999catastrophic}.
+This problem is significant in the domain of natural language understanding (NLU) as well.
+
+Humans are remarkable at using their previously acquired knowledge when learning a new language task.
+For instance, children first learn a language by mostly observing and listening to their parents.
+They bolster their language skills through curricula by learning more formal language rules like grammar and syntax.
+Using their linguistic knowledge, they can comprehend intricate texts and can answer questions based on them.
+They can further infer meanings of natural language sentences used in complex contexts.
+In all the stages of human learning, we are exceptionally good at retaining important parts of our previous knowledge.
+
+In order to design real-world self-learning systems, two requirements are essential -- adaptability to learn new knowledge and stability while evolving and integrating it.
+Therefore a the ratio of \textit{how plastic} and \textit{how static} a system is decides how adaptable and how stable it is, respectively.
+A balance needs to be maintained to alleviate the problem of CF of consolidated knowledge, which gives rise to the \textit{stability-plasticity dilemma}.
+
+On the other hand, deep learning based language models drastically forget their previous knowledge while learning new tasks.
+Current state of the art language models, like BERT \cite{DBLP:journals/corr/abs-1810-04805}, struggle to learn multiple tasks in an online fashion \cite{DBLP:journals/corr/abs-1901-11373}.
+Despite having a huge capacity, these models cannot learn multiple tasks effectively due to CF.
+
+In the current literature, after pre-training a language model, it is fine-tuned on each downstream task separately.
+While evaluating a language model, performance metrics like accuracy and F1 score are reported separately for each downstream task.
+In this paper, we argue against this kind of evaluation of language models.
+Language models need to be evaluated on multiple tasks trained in a continual way and on metrics measuring knowledge retention capacity apart from accuracy and F1.
+We further put forward an argument that retaining and reusing the linguistic knowledge and avoiding CF is an important characteristic of general linguistic intelligence.
+
+Our work in this paper mostly focuses on evaluating BERT-base trained on multiple tasks based on two metrics namely (i) backward transfer and (ii) forward transfer proposed in \citeauthor{DBLP:journals/corr/Lopez-PazR17}.
+We compare vanilla fine-tuning of BERT-base with continual fine-turning based on neuroscience inspired techniques like Elastic Weight Consolidation (EWC, \citealt{DBLP:journals/corr/KirkpatrickPRVD16}), Memory Aware Synapses(MAS, \citealt{aljundi2018memory}) and Synaptic Intelligence (SI, \cite{Cortes2017AdaNetAS}).
+As per our knowledge, this is the first work attempting to enable language models to learn downstream tasks in an online fashion and evaluating them based on the metrics mentioned above.
+
+\section{Related Work}
+\label{sec:related}
+
+There has been multiple ways proposed to mitigate CF in connectionist networks. The paper segregates and reviews some of them into the following categories.
+
+\subsection{Memory based methods}
+Memory methods involve \textit{rehearsing} on old samples along with seeing new distribution data interleaved \cite{Robins1995CatastrophicFR, Gepperth2016ABI}.
+These methods although cure the forgetting better than other methods, but this involves storing past events explicitly, which makes it difficult to scale as the neural networks becomes very large.
+% which is the case for most state-of-the-art architectures 
+% (e.g. BERT $\sim$ 340M parameters \cite{DBLP:journals/corr/abs-1810-04805}, FixEfficientNet $\sim$ 480M parameters \cite{touvron2019fixing}, etc). 
+Also, this approach does not consider the fact that a network needs to learn unknown number of future tasks, which makes choosing \textit{defining set of examples} per task for storing in a fixed resourced system complicated.
+
+\subsection{Regularization based methods}
+These methods cure CF by enforcing a cost-based constraint during the update step of the network weights.
+These approaches aim to change a subset or all of the current parameters to an optimal value that works well for both the previous tasks and the current new task.
+
+\citet{Li2018LearningWF} proposed \textit{Learning without Forgetting (LwF)} for convolutional neural networks.
+This approach optimizes the new task parameters, while additionally optimizing the predictions made by the shared parameters, does not deviate much from previous predictions.
+The loss function while optimizing for each new parameter, minimizes the difference between new output and old output predictions as though learning the old task again.
+% % The following equation illustrates the optimization step used in LwF,
+
+% \begin{equation}
+% \begin{split}
+% \theta^*_s,\theta^*_o,\theta^*_n \leftarrow \text{argmin}_{\hat{\theta}_s,\hat{\theta}_o,\hat{\theta}_n} [ \lambda_o \mathcal{L}_{old}(Y_o,\hat{Y}_o) \\ +
+% \mathcal{L}_{new}(Y_n,\hat{Y}_n) + \mathcal{R}(\hat{\theta}_s,\hat{\theta}_o,\hat{\theta}_n)],
+% \end{split}
+% \end{equation}
+
+% where $\mathcal{L}_{old}(Y_o,\hat{Y}_o)$ and $\mathcal{L}_{new}(Y_n,\hat{Y}_n)$ represent the difference between the predicted values $\hat{Y}$ and the ground truth values $Y$ of the old and new tasks, respectively using parameters $\hat{\theta}_s,\hat{\theta}_o $ and  $\hat{\theta}_n$.
+$\lambda_o$ is used to balance previous and current tasks, and $\mathcal{R}$ is a regularization term to prevent overfitting.
+After the optimization, a new smaller model is trained using knowledge distillation which works optimally as a multi-task model for all learned tasks.
+The requirement of storing data from previous tasks is its biggest disadvantage.
+
+\citet{DBLP:journals/corr/KirkpatrickPRVD16} proposed  \textit{Elastic Weight Consolidation (EWC)} constrains each parameter based on how important it is in the original task, which results in model that is flexible for adapting to new tasks while maintaining the performance on previous task.
+Per-parameter significance is calculated using the diagonal of the Fischer information matrix, which is an approximation of the second derivative of loss with respect to each parameter.
+This approximation is linear to compute in the number of parameters and training examples.
+
+The final parameters are calculated as follows:
+
+\begin{equation}
+\theta_N^* \leftarrow \text{argmin}_{\theta} L_N(\theta) + \sum_i \dfrac{\lambda}{2} (\dfrac{dL_{Pi}(\theta_{Pi})}{d\theta_{Pi}})^2(\theta - \theta_{Pi})^2 
+\end{equation}
+
+where $\theta_N^*$ are the optimal parameters after training on new task.
+$L_N(\theta)$ is the loss metric for new task, $dL_{Pi}(\theta_{Pi})$ is the loss metric for previous(i-th) task, $\theta_{Pi} $ are the optimal parameters until i-th task.
+$\lambda$ is the importance parameter for old tasks.
+
+ \citet{aljundi2018memory} proposed \textit{Memory Aware Synapses} inspired by Hebbian learning in natural systems.
+The core idea is to learn which parts of the model parameters are important relative to others, using unlabelled data itself.
+They calculate importance weights $\Omega_{ij}$ for all parameters $\theta_{ij}$, where $i$ and $j$ are indices of pairs of neurons $n_i$ and $n_j$ residing in two consecutive layers, respectively.
+The importance weight represent the \textit{sensitivity} of the function output of a learned function, $F:X_n \longrightarrow Y_n$, to changes in the corresponding parameter.
+Therefore,
+
+\begin{equation}
+\Omega_{ij} =\frac{1}{N}\sum_{k=1}^N  \mid\mid g_{ij}(x_k) \mid\mid
+\end{equation}
+where, $N$ is the number of data points at a given stage and
+\begin{equation}
+g_{ij}(x_k)=\frac{\partial (F(x_k; \theta))}{\partial \theta_{ij}}
+\end{equation}
+
+for a given data point $x_k$.
+Therefore, whichever parameters have lower importance can be changed without degrading the accuracy on previous tasks, while decreasing the loss for subsequent tasks.
+Thus, if we wish to learn a new task, the total loss function $L(\theta)$ becomes,
+
+\begin{equation}
+L(\theta)=L_n(\theta)+{\lambda} \sum_{i,j} \Omega_{ij}(\theta_{ij}-\theta^*_{ij})^2
+\end{equation}
+
+where, $L_n(\theta)$ is the new task loss, $\theta^*_{ij}$ are the old parameters and $\lambda$ is a regularizer hyperparamter.
+
+ \citet{DBLP:journals/corr/ZenkePG17} \textit{Synaptic Intelligence} loss is similar to MAS: 
+ \begin{align*}
+     L(\theta) &=L_n(\theta)+{\lambda} \sum_{k} \Omega_k^{\mu} (\theta - \theta_k)^2,\\ 
+     where:
+     \Omega_k^{\mu} &= \sum_{v<\mu} \dfrac{\omega_k^v}{(\Delta_k^v)^2+\epsilon} \\
+     \omega_k^v &= \int_{t^{\mu-1}}^{t^{\mu}} g_k(t)\theta^{'}_k(t)
+ \end{align*}
+Here k signifies task number, $g_k(t)$ is the gradient of loss w.r.t parameter k, $\theta^{'}_k(t)$ is the parameter change at time t
+
+In case of SI the importance of parameter is an accumulation of product of gradient and parameter change.
+It depends on two quantities: 1) $ \omega_k^v $ is a drop in loss over the trajectory of training.
+2) How far the loss has changed $\Delta_k^v = \theta_k(t^v) - \theta_k(t^{v-1})$.
+
+\subsection{Dynamic Architectures} 
+In this approach, a network is augmented as new tasks and more neural resources are needed \cite{Rusu2016ProgressiveNN, Cortes2017AdaNetAS}.
+Old network parameters are fully preserved to prevent CF and additional neurons are added and trained separately.
+Although this approach works well for reinforcement learning tasks but leads to higher complexity of architecture as the number of learned tasks increases.
+% proposed a model augmentation technique named \textit{Progressive Networks}, in which the old network parameters are preserved to prevent CF and when a new task needs to be learned, a new network is trained and coalesced into the old network by forming lateral connections.
+This approach although works well on reinforcement learning tasks, but leads
+
+% \citet{Cortes2017AdaNetAS} proposed a technique similar to neural architectural search named \textit{AdaNet}, in which they optimize both structure and weights of networks starting with a general structure.
+The models adapts itself as newer tasks are learned.
+The approach balances the model complexity by merging similar features to obtain compact feature representations and scaling up when more neural resources are needed.
+
+\section{Proposed Method}
+\label{sec:prop_method}
+
+\subsection{Evaluation Metrics}
+\label{sec:metric}
+This paper uses two metrics proposed by \citeauthor{DBLP:journals/corr/Lopez-PazR17}. They are:
+\begin{enumerate}
+    \item \textit{Backward transfer (BWT)} is the influence of learning a new task $T$ on the previous $i$ tasks. 
+    \item \textit{Forward transfer (FWT)} is the influence of learning a new task $T$ on future $i$ tasks.
+\end{enumerate}
+
+The paper defines $R$ as the accuracy matrix and $Tr$ as the transfer matrix, where $R_{i, j}$ is the test classification accuracy of the model on task $t_j$ after observing the last data point from task $t_i$ and $Tr_{i, j}}$ is the backward transfer when $i > j$ and the forward transfer when $i < j$, respectively.
+
+\subsection{Continual Framework}
+
+The paper proposes a continual framework for learning multiple downstream tasks on BERT and illustrates in Algorithm \ref{algo:1}.
+Let $\theta_{B}$ be BERT pre-trained parameters\footnote{https://github.com/huggingface/transformers}.
+In case of vanilla fine-tuning, for each task, task-specific head are initialized to zero and BERT-specific parameters are re-initialized to $\theta_{B}$.
+But, in this framework, BERT-specific parameters are \textit{not re-initialized}, when training new tasks.
+
+Let us say we are fine-tuning BERT on $n$ downstream tasks ($T_i, 1<=i<=n $).
+Before training the first task, we initialize BERT-specific parameters to $\theta_{B}$.
+Since, we are not updating BERT-specific parameters, after training task $T_i$, let us say our BERT-specific parameters are  $\theta_{Bi}$.
+When training a new task $T_{i+1}$, we attach freshly initialized task-specific head with parameters $\theta_{Ti}$ = $\theta_{Bi}$.
+When training a new task, $T_{i+1}$, we use techniques like EWC, MAS and SI to consolidate the previous BERT-specific parameters $\theta_{Bi}$.
+Consolidating previous parameters helps us retain knowledge obtained from previously trained tasks.
+
+While evaluating our model, we report accuracy on task $T_i$ after re-installing its task-specific head.
+More formally, after training a task $T_i$, we evaluate backward transfer for all previous tasks ($T_j, j<i$) and forward transfer for all future tasks ($T_j, j>i$).
+We store backward and forward transfers in a $N \times N$ transfer matrix obtained from $R$.
+Very high negative backward transfer is called catastrophic forgetting which is observed in vanilla fine-turning.
+But, using techniques like EWC, significantly reduced negative backward transfer.
+Discussion about forward transfer and its significance is left to future work.
+
+\begin{algorithm}
+    $T \leftarrow \mbox{Tasks}$ \\
+    $N \leftarrow \mbox{Number of Tasks}$ \\
+    $\theta_B \leftarrow \mbox{Bert Pre-trained Parameters}$\\
+    $R \leftarrow 0_{N \times N}$ \Comment{;Test Accuracy Matrix}\\
+    $Tr \leftarrow 0_{N \times N}$ \Comment{;Transfer Matrix}\\
+  \For{$i = 1:N$}{
+    $D_i \leftarrow data(T_{i, train})$ \\
+    \theta_i = argmin_{\theta} L_t(D_i,  \theta_B; \theta_1, ..., \theta_{i-1})\\
+    \theta_{B_i}, \theta_{T_i} = seperate(\theta_i) \\
+    \For{$j = 1:T$}{
+        $D_{test} \leftarrow data(T_{j, test})$ \\
+        $R_{i,j} \leftarrow acc(\theta_{Bi}, \theta_{Tj}, D_{test})$ \\
+        % \If{i \neq j}
+        %     \State 
+        $Tr_{i, j} \leftarrow R_{i, j} - R_{i, i}$ \\
+        % \ElseIf{i $>$ j} 
+        %     \State $Tr_{i, j} \leftarrow R_{j, i} - R_{i, i}$ \\
+        % \EndIf % {}{\ifthenelse{i $>$ j}{}{}}
+        % \\
+    }
+    }
+    \textbf{return} $R, Tr$
+    \caption{Proposed Framework}
+    \label{algo:1}
+\end{algorithm}
+
+\subsection{Data}
+\label{sec:data}
+
+In this paper we work in three phases using various GLUE tasks \cite{wang2019glue}, as follows:
+\begin{itemize}
+  \item \textbf{First Phase (Two low data tasks):} Microsoft Research Paraphrase Corpus (MRPC) and Recognizing Textual Entailment (RTE).
+  \item \textbf{Second Phase (Two high data tasks):} Quora Question Pairs (QQP) and Multi Natural Language Inference (MNLI), and vice-versa.
+  \item \textbf{Final Phase (All tasks):} More than two tasks -- MRPC $\rightarrow$ RTE $\rightarrow$ MNLI-mm.
+\end{itemize}
+
+\section{Results}
+\label{sec:results}
+
+We obtained results for baseline and EWC, for the \textbf{first phase}.
+Our baseline results strengthen our hypothesis that the models suffer from very high negative backward transfer.
+Forward transfer is still low and methods to improve it will be discussed in the future work.
+Table 1 shows the results on both vanilla fine-turning (baseline) and continual fine-turning with EWC.
+The model trained with EWC has relatively lower negative backward transfer compared to baseline.
+We are expecting similar results from MAS and SI.
+
+% Results for second phase final phase will also be shown in the future work. MAS and SI are work in progress.
+
+% \subsection{First Phase}
+
+% Baseline and EWC results are done for first phase. Accuracy and transfer for the first phase configuration (MRPC - RTE) is shown below. Results are reported after 2 epochs.
+
+% \textbf{Baseline Matrix:}
+
+% \begin{center}
+%  \begin{tabular}{||c c c||} 
+%  \hline
+%  Task & MRPC & RTE  \\ [0.5ex] 
+%  \hline\hline
+%  MRPC & 0.86(CT) & 0.52(\textbf{FT} -0.12) \\ 
+%  \hline
+%  RTE & 0.65(\textbf{BT} -0.21) & 0.64(CT) \\ [1ex] 
+%  \hline
+% \end{tabular}
+% \end{center}
+
+% \textbf{EWC Matrix:}
+
+% \begin{center}
+
+% \end{center}
+
+\begin{table}[h!]
+\centering
+ \begin{tabular}{|c|c|c|} 
+ \hline
+ \textbf{Task} & \textbf{MRPC} & \textbf{RTE}  \\
+ \hline\hline
+ & \textit{Baseline} & \\
+ \hline
+ \textbf{MRPC} & 0.86(CT) & 0.52(FT -0.12) \\ 
+ \hline
+ \textbf{RTE} & 0.65(BT -0.21) & 0.64(CT) \\ % [1ex] 
+ \hline
+ & \textit{EWC} & \\ 
+ \hline\hline
+ \textbf{MRPC} & 0.87(CT) & 0.52(FT -0.12) \\ 
+ \hline
+ \textbf{RTE} & 0.75(BT -0.12) & 0.64(CT) \\ %[1ex] 
+ \hline
+% \caption{Table A}
+\end{tabular}
+
+%  \begin{tabular}{|c|c|c|} 
+%  \hline
+
+% % \caption{Table A}
+% \end{tabular}
+% % \end{center}
+\caption{\label{base-table} Results for baseline and EWC; \textbf{CT:} Current Task, \textbf{BT:} Backward Transfer, \textbf{FT:} Forward Transfer. 
+ }
+\end{table}
+
+\section*{Availability}
+The code and \LaTeX{} source files are available at \url{https://github.com/mittalgovind/continual-learning-nlu}.
+% \section{Conclusion}
+% \label{sec:conc}
+
+\section*{Collaboration Statement}
+The contributions of the authors, in the same order, are as follows:
+
+\textit{Mohith Damarapati*:} Implemented EWC (Elastic Weight Consolidation) from scratch.
+Designed a framework to evaluate models in a continual way (i.e.
+print both backward and forward transfers after training each task).
+Fixed some crucial bugs that hindered our project progress.
+
+\textit{Govind Mittal*:} Implemented Memory Aware Synapses (MAS) for BERT from scratch. Wrote the complete related work (Sec. \ref{sec:related} and part of introduction (Sec. \ref{sec:intro}).
+
+\textit{Chandra Prakash Konkimalla*:} Implemented the baseline framework for finetuning the tasks one after another.
+Fixed bugs in EWC (Elastic Weight Consolidation) training procedure.
+Integrated Baseline and EWC into one code so that the results can be consistent.
+
+\textit{Aakriti Gupta:} No contribution to team yet. Still working on SI.
+
+* = equal contribution
 \bibliography{paper}

### 2020-04-22 SI/arguments.py
Added Runner code for SI

@@ -1,0 +1,64 @@
+import argparse
+import json
+import torch
+
+def parse_args():
+	parser = argparse.ArgumentParser()
+	parser.add_argument("--data_dir", 
+						type=str,
+						default="../data",
+						required=True,
+						)
+	parser.add_argument("--task_params", 
+						type=str,
+						required=True,
+						help="JSON file path"
+						)
+	parser.add_argument("--output_dir", 
+						type=str,
+						default="./output",
+						required=True,
+						)
+	parser.add_argument("--per_gpu_batch_size", 
+						default=8, 
+						type=int, 
+						help="Batch size per GPU",
+						)
+	parser.add_argument("--cuda", 
+						action="store_true",
+						)
+	parser.add_argument("--tokenizer_name", 
+						type=str,
+						required=True,
+						)
+	parser.add_argument("--do_lower_case", 
+						action="store_true",
+						)
+	parser.add_argument("--model_type",
+						default=None,
+						type=str,
+						required=True,
+						)
+	parser.add_argument("--max_seq_length",
+						default=128,
+						type=int,
+						)
+	parser.add_argument("--num_train_epochs",
+						default=1,
+						type=int,
+						)
+	parser.add_argument("--seed",
+						default=42,
+						type=int,
+						)
+
+	args = parser.parse_args()
+	with open(args.task_params) as file:
+		args.task_params = json.load(file)
+	if args.cuda:
+		args.device = torch.device("cuda")
+		args.n_gpu = torch.cuda.device_count()
+	else:
+		args.device = torch.device("cpu")
+		args.n_gpu = 0
+	return args

### 2020-04-22 SI/keras_utils.py

@@ -1,0 +1,109 @@
+# Copyright (c) 2017 Ben Poole & Friedemann Zenke
+# MIT License -- see LICENSE for details
+#
+# This file is part of the code to reproduce the core results of:
+# Zenke, F., Poole, B., and Ganguli, S. (2017). Continual Learning Through
+# Synaptic Intelligence. In Proceedings of the 34th International Conference on
+# Machine Learning, D. Precup, and Y.W. Teh, eds. (International Convention
+# Centre, Sydney, Australia: PMLR), pp. 3987-3995.
+# http://proceedings.mlr.press/v70/zenke17a.html
+#
+
+# Keras-specific functions and utils
+from keras.callbacks import Callback
+from keras.models import Model
+import keras.backend as K
+from keras.layers import Dense
+import tensorflow as tf
+
+class LossHistory(Callback):
+    def __init__(self, *args, **kwargs):
+        super(LossHistory, self).__init__(*args, **kwargs)
+        self.losses = []
+        self.regs = []
+
+    def on_batch_end(self, batch, logs={}):
+        self.losses.append(logs.get('loss'))
+        self.regs.append(K.get_session().run(self.model.optimizer.regularizer))
+
+
+# Create a callback that tracks FisherInformation
+from keras.models import Model
+import keras.backend as K
+def compute_fishers(model):
+    # Check that model only contains Dense layers
+    for l in model.layers:
+        if not isinstance(l, Dense):
+            raise ValueError("All layers of the model must be Dense, got %s"%l)
+    # Create new model used to extract activations at each layer
+    new_model = Model(inputs=model.input, outputs=[l.output for l in model.layers])
+    acts = new_model(model.input)
+
+    out = acts[-1]
+    out_dim = out.get_shape().as_list()[-1]
+    #assert len(model.weights) %2 == 0
+    n_weights = len(model.weights) // 2
+
+
+    def _get_fishers():
+        fisher_weights = [0.0] * n_weights
+        fisher_biases = [0.0] * n_weights
+        for idx in range(out_dim):
+            # Clips output
+            # https://github.com/fchollet/keras/blob/master/keras/backend/tensorflow_backend.py#L2743
+            output = out[:, idx]
+            epsilon = tf.convert_to_tensor(x)
+            if epsilon.dtype != output.dtype.base_dtype:
+                epsilon = tf.cast(epsilon, output.dtype.base_dtype)
+
[…]

### 2020-04-22 SI/main.py

@@ -1,0 +1,597 @@
+import random
+import numpy as np
+import torch
+import logging
+import os
+import json
+from torch.nn import functional as F
+from torch import autograd
+from torch.autograd import Variable
+from torch.utils.data.dataloader import default_collate
+from transformers import BertModel
+from transformers.modeling_bert import BertPreTrainedModel
+from transformers.file_utils import add_start_docstrings, add_start_docstrings_to_callable
+from torch.utils.data import DataLoader, RandomSampler, SequentialSampler, TensorDataset
+from arguments import parse_args
+from tqdm import tqdm, trange
+from collections import OrderedDict 
+
+from transformers import (
+    MODEL_FOR_SEQUENCE_CLASSIFICATION_MAPPING,
+    WEIGHTS_NAME,
+    AdamW,
+    AutoConfig,
+    AutoModelForSequenceClassification,
+    AutoTokenizer,
+    get_linear_schedule_with_warmup,
+)
+from transformers import glue_compute_metrics as compute_metrics
+from transformers import glue_convert_examples_to_features as convert_examples_to_features
+from transformers import glue_output_modes
+from transformers import glue_processors
+from torch import nn
+from torch.nn import CrossEntropyLoss, MSELoss
+import tensorflow as tf
+import keras.activations as activations
+from keras.optimizers import Adam, RMSprop, SGD
+from keras.callbacks import Callback
+import copy
+import keras.backend as K
+import keras.activations as activations
+from keras.models import Sequential
+from keras.layers import Dense, Dropout, Activation, Flatten
+from keras.layers import Conv2D, MaxPooling2D
+
+import utils
+from keras_utils import LossHistory
+
+try:
+    from torch.utils.tensorboard import SummaryWriter
+except ImportError:
+    from tensorboardX import SummaryWriter
+
+
+from utils import convert_dict
+
+n_tasks = 6
+output_dim = 10*n_tasks
+nb_classes = output_dim
+
+# tf.reset_default_graph()
+
+config = tf.ConfigProto()
+config.gpu_options.allow_growth=True
+sess = tf.InteractiveSession(config=config)
+sess.run(tf.global_variables_initializer())
+
+
+logger = logging.getLogger(__name__)
+
+
+
+select = tf.select if hasattr(tf, 'select') else tf.where
[…]

### 2020-04-22 SI/utils.py

@@ -1,0 +1,563 @@
+#!/usr/bin/python
+# Copyright (c) 2017 Ben Poole & Friedemann Zenke
+# MIT License -- see LICENSE for details
+#
+# This file is part of the code to reproduce the core results of:
+# Zenke, F., Poole, B., and Ganguli, S. (2017). Continual Learning Through
+# Synaptic Intelligence. In Proceedings of the 34th International Conference on
+# Machine Learning, D. Precup, and Y.W. Teh, eds. (International Convention
+# Centre, Sydney, Australia: PMLR), pp. 3987-3995.
+# http://proceedings.mlr.press/v70/zenke17a.html
+#
+"""Utility functions for benchmarking online learning"""
+from __future__ import division
+import numpy as np
+import keras
+from keras.utils import np_utils
+
+from keras.datasets import mnist, cifar10, cifar100
+from keras.optimizers import Adam, RMSprop, SGD
+import keras.backend as K
+
+import pickle
+import gzip
+
+import tensorflow as tf
+
+
+
+
+class AttrDict(dict):
+	def __init__(self, *args, **kwargs):
+		super(AttrDict, self).__init__(*args, **kwargs)
+		self.__dict__ = self
+
+def convert_dict(config, args):
+	out = AttrDict()
+	out.update(config)
+	out.update({
+				"num_train_epochs" : args.num_train_epochs,
+				"seed" : args.seed,
+				"n_gpu" : args.n_gpu,
+				"per_gpu_batch_size" : args.per_gpu_batch_size,
+				"warmup_steps" : 0,
+				"model_name_or_path" : "",
+				"device" : args.device,
+				"model_type" : args.model_type,
+				"output_dir" : args.output_dir,
+				"data_dir" : args.data_dir,
+				"max_seq_length" : args.max_seq_length
+				})
+	return out
+
+
+
+
+def ema(decay, prev_val, new_val):
+	"""Compute exponential moving average.
+
+    Args:
+        decay: 'sum' to sum up values, otherwise decay in [0, 1]
+        prev_val: previous value of accumulator
+        new_val: new value
+    Returns:
+        updated accumulator
+    """
+	if decay == 'sum':
+		return prev_val + new_val
+	return decay * prev_val + (1.0 - decay) * new_val
+
+
+def leak(decay, prev_val, new_val):
+	"""Compute leaky integrator.
+
+    Like ema, but expectation value depends on decay time constant.
+
+    Args:
[…]

### 2020-04-23 paper/paper.tex
partial draft updated

@@
 \begin{enumerate}
-    \item \textit{Backward transfer (BWT)} is the influence of learning a new task $T$ on the previous $i$ tasks. 
-    \item \textit{Forward transfer (FWT)} is the influence of learning a new task $T$ on future $i$ tasks.
+    \item \textit{Backward transfer (BWT)} is the influence of learning a new task on the previous tasks. 
+    \item \textit{Forward transfer (FWT)} is the influence of learning a new task on future tasks.
+    \item \textit{Accuracy} is the test classification accuracy on the current new task.
 \end{enumerate}
 
-The paper defines $R$ as the accuracy matrix and $Tr$ as the transfer matrix, where $R_{i, j}$ is the test classification accuracy of the model on task $t_j$ after observing the last data point from task $t_i$ and $Tr_{i, j}}$ is the backward transfer when $i > j$ and the forward transfer when $i < j$, respectively.
+The paper defines $R$ as the accuracy matrix and $Tr$ as the transfer matrix, where $R_{i, j}$ is the test classification accuracy of the model on task $t_j$ after observing the last data point from task $t_i$ and $Tr_{i, j}$ is the backward transfer when $i > j$ and the forward transfer when $i < j$, respectively.
 
 \subsection{Continual Framework}
-
-The paper proposes a continual framework for learning multiple downstream tasks on BERT and illustrates in Algorithm \ref{algo:1}.
-Let $\theta_{B}$ be BERT pre-trained parameters\footnote{https://github.com/huggingface/transformers}.
-In case of vanilla fine-tuning, for each task, task-specific head are initialized to zero and BERT-specific parameters are re-initialized to $\theta_{B}$.
-But, in this framework, BERT-specific parameters are \textit{not re-initialized}, when training new tasks.
-
-Let us say we are fine-tuning BERT on $n$ downstream tasks ($T_i, 1<=i<=n $).
-Before training the first task, we initialize BERT-specific parameters to $\theta_{B}$.
-Since, we are not updating BERT-specific parameters, after training task $T_i$, let us say our BERT-specific parameters are  $\theta_{Bi}$.
-When training a new task $T_{i+1}$, we attach freshly initialized task-specific head with parameters $\theta_{Ti}$ = $\theta_{Bi}$.
-When training a new task, $T_{i+1}$, we use techniques like EWC, MAS and SI to consolidate the previous BERT-specific parameters $\theta_{Bi}$.
-Consolidating previous parameters helps us retain knowledge obtained from previously trained tasks.
-
-While evaluating our model, we report accuracy on task $T_i$ after re-installing its task-specific head.
-More formally, after training a task $T_i$, we evaluate backward transfer for all previous tasks ($T_j, j<i$) and forward transfer for all future tasks ($T_j, j>i$).
-We store backward and forward transfers in a $N \times N$ transfer matrix obtained from $R$.
-Very high negative backward transfer is called catastrophic forgetting which is observed in vanilla fine-turning.
-But, using techniques like EWC, significantly reduced negative backward transfer.
-Discussion about forward transfer and its significance is left to future work.
 
@@
     $N \leftarrow \mbox{Number of Tasks}$ \\
-    $\theta_B \leftarrow \mbox{Bert Pre-trained Parameters}$\\
+    $\theta_{B_0} \leftarrow \mbox{Bert Pre-trained Parameters}$\\
     $R \leftarrow 0_{N \times N}$ \Comment{;Test Accuracy Matrix}\\
@@
     $D_i \leftarrow data(T_{i, train})$ \\
-    \theta_i = argmin_{\theta} L_t(D_i,  \theta_B; \theta_1, ..., \theta_{i-1})\\
-    \theta_{B_i}, \theta_{T_i} = seperate(\theta_i) \\
+    $\theta_{B_i}, \theta_{T_i}$ \leftarrow $\mbox{argmin}_{\theta_B, \theta_T} L(D_i,  \theta_{B_{i-1}}, \theta_{T_i})$\\
     \For{$j = 1:T$}{
@@
         $R_{i,j} \leftarrow acc(\theta_{Bi}, \theta_{Tj}, D_{test})$ \\
-        % \If{i \neq j}
-        %     \State 
         $Tr_{i, j} \leftarrow R_{i, j} - R_{i, i}$ \\
-        % \ElseIf{i $>$ j} 
-        %     \State $Tr_{i, j} \leftarrow R_{j, i} - R_{i, i}$ \\
-        % \EndIf % {}{\ifthenelse{i $>$ j}{}{}}
-        % \\
     }
@@
 \end{algorithm}
+
+The paper proposes a continual framework for learning multiple downstream tasks on BERT and illustrates in Algorithm \ref{algo:1}.
+Let $T$ be the tasks to be learned, $N$ be the number of tasks to be learned, $\theta_{B_0}$ be BERT pre-trained parameters obtained from huggingface\footnote{https://github.com/huggingface/transformers}, $R$ is the accuracy matrix and $Tr$ is the transfer matrix, both initialized to zero.
+
+In case of vanilla fine-tuning, after each task-specific head are initialized randomly and BERT-specific parameters (All BERT parameters except the task specific ones) are re-initialized to $\theta_{B_0}$.
+But, in this framework, BERT-specific parameters  are \textit{not re-initialized}, when training new tasks.
+
+The paper fine-tunes BERT on $N$ downstream tasks $T_i, \forall i \in [1, N]$.
+Before training the first task, BERT-specific parameters are initialized to $\theta_{B_0}$.
+After starting the training loop, the task-specific training data is loaded.
+Since, we are not updating BERT-specific parameters, after any training task $T_i$, let it be $\theta_{B_i}$.
+When training a new task $T_{i+1}$, a randomly initialized task-specific head with parameters $\theta_{T_{i+1}}$ is attached to previously trained $\theta_B_{i}$.
+
+When learning a new task, $T_{i+1}$, techniques like EWC, MAS and SI are employed to consolidate the previous trained parameters $\theta_{B_i}$.
+Consolidating previous parameters helps us to retain knowledge obtained from previously trained tasks.
+
+While evaluating the model, test accuracy on task $T_i$ after re-installing its task-specific head is reported.
+After training a task $T_i$, backward transfer for all previous tasks ($T_j, \forall j<i$) and forward transfer for all future tasks ($T_j, \forall j>i$) is evaluated.
+Backward and forward transfers are obtained from $R$ and stored in an $N \times N$ transfer matrix $Tr$.
 
@@
 Forward transfer is still low and methods to improve it will be discussed in the future work.
-Table 1 shows the results on both vanilla fine-turning (baseline) and continual fine-turning with EWC.
+Table 1 shows the results for both vanilla fine-turning (baseline) and continual fine-turning with EWC.
 The model trained with EWC has relatively lower negative backward transfer compared to baseline.
-We are expecting similar results from MAS and SI.
+We are expecting to further mitigate negative backward transfer with MAS and SI.
 

### 2020-04-25 MAS/main.py
modified:   MAS/main.py 	modified:   MAS/mas_utils.py 	modified:   MAS/optimizer_lib.py

@@ -4,8 +4,11 @@ import torch
 import logging
 import os
 import json
-
+from torch.nn import functional as F
+from torch import autograd
 from torch.autograd import Variable
+from torch.utils.data.dataloader import default_collate
+
 from torch.utils.data import DataLoader, RandomSampler, SequentialSampler, TensorDataset
 from arguments import parse_args
 from tqdm import tqdm, trange
@@ -24,29 +27,27 @@ from transformers import glue_compute_metrics as compute_metrics
 from transformers import glue_convert_examples_to_features as convert_examples_to_features
 from transformers import glue_output_modes
 from transformers import glue_processors
+import copy
 
 try:
     from torch.utils.tensorboard import SummaryWriter
 except ImportError:
     from tensorboardX import SummaryWriter
 
+# MAS-SPECIFIC IMPORTS
 from dict_utils import convert_dict
-
-from pdb import set_trace
-
-# MY IMPORTS
 from mas_utils import init_reg_params, shared_model, exp_lr_scheduler, compute_omega_grads_norm, \
     init_reg_params_across_tasks, consolidate_reg_params
-from optimizer_lib import local_sgd, omega_update
+from optimizer_lib import local_sgd, omega_update_Adam, local_AdamW
 
 logger = logging.getLogger(__name__)
-logger.propagate = False
 
 
 def set_seed(seed, n_gpu):
     random.seed(seed)
     np.random.seed(seed)
     torch.manual_seed(seed)
+    torch.cuda.manual_seed(seed)
     if n_gpu > 0:
         torch.cuda.manual_seed_all(seed)
 
@@ -66,7 +67,7 @@ def save_model(args, task_num, model):
 
     torch.save(bert_paramters, os.path.join(args.output_dir, "bert_paramters_" + str(task_num) + ".pt"))
     torch.save(task_paramters, os.path.join(args.output_dir, "task_paramters_" + str(task_num) + ".pt"))
-    torch.save(model.reg_params, os.path.join(args.output_dir, "reg_params_{}.pt".format(task_num)))
+
     print()
     print("***** Parameters Saved for task", task_num, "*****")
     print()
@@ -75,7 +76,6 @@ def save_model(args, task_num, model):
 def train(args, train_dataset, task, all_tasks, model, task_num, tokenizer, accuracy_matrix):
     """ Train the model """
     tb_writer = SummaryWriter()
-
     args.train_batch_size = args.per_gpu_batch_size * max(1, args.n_gpu)
     train_sampler = RandomSampler(train_dataset)
[…]

### 2020-04-25 MAS/mas_utils.py

@@ -58,7 +58,7 @@ def exp_lr_scheduler(optimizer, epoch, init_lr=0.0008, lr_decay_epoch=20):
 
     """
     lr = init_lr * (0.1 ** (epoch // lr_decay_epoch))
-    # print('lr is ' + str(lr))
+    print('lr is ' + str(lr))
 
     # if (epoch % lr_decay_epoch == 0):
     #     print('LR is set to {}'.format(lr))
@@ -205,6 +205,7 @@ def compute_omega_grads_norm(model, dataloader, optimizer, device):
 
         # optimizer.step computes the omega values for the new batches of data
         optimizer.step(model.reg_params, index, len(batch[0]), device)
+        # optimizer.step(model.reg_params)
         del batch
         index = index + 1
 

### 2020-04-25 MAS/optimizer_lib.py

@@ -2,7 +2,7 @@
 # coding: utf-8
 
 from __future__ import print_function
-
+import math
 import torch
 import torch.nn as nn
 import torch.optim as optim
@@ -16,6 +16,109 @@ import os
 import shutil
 
 
+class local_AdamW(optim.Optimizer):
+    """ Implements Adam algorithm with weight decay fix.
+    Parameters:
+        lr (float): learning rate. Default 1e-3.
+        betas (tuple of 2 floats): Adams beta parameters (b1, b2). Default: (0.9, 0.999)
+        eps (float): Adams epsilon. Default: 1e-6
+        weight_decay (float): Weight decay. Default: 0.0
+        correct_bias (bool): can be set to False to avoid correcting bias in Adam (e.g. like in Bert TF repository). Default True.
+    """
+
+    def __init__(self, params, reg_lambda, lr=1e-3, betas=(0.9, 0.999), eps=1e-6, weight_decay=0.0, correct_bias=True):
+        if lr < 0.0:
+            raise ValueError("Invalid learning rate: {} - should be >= 0.0".format(lr))
+        if not 0.0 <= betas[0] < 1.0:
+            raise ValueError("Invalid beta parameter: {} - should be in [0.0, 1.0[".format(betas[0]))
+        if not 0.0 <= betas[1] < 1.0:
+            raise ValueError("Invalid beta parameter: {} - should be in [0.0, 1.0[".format(betas[1]))
+        if not 0.0 <= eps:
+            raise ValueError("Invalid epsilon value: {} - should be >= 0.0".format(eps))
+        defaults = dict(lr=lr, betas=betas, eps=eps, weight_decay=weight_decay, correct_bias=correct_bias)
+        super().__init__(params, defaults)
+        self.reg_lambda = reg_lambda
+
+    def step(self, reg_params, closure=None):
+        """Performs a single optimization step.
+        Arguments:
+            closure (callable, optional): A closure that reevaluates the model
+                and returns the loss.
+        """
+        loss = None
+        if closure is not None:
+            loss = closure()
+
+        for group in self.param_groups:
+            for p in group["params"]:
+                if p.grad is None:
+                    continue
+                grad = p.grad.data
+                if grad.is_sparse:
+                    raise RuntimeError("Adam does not support sparse gradients, please consider SparseAdam instead")
+
+                state = self.state[p]
+
+                # State initialization
+                if len(state) == 0:
+                    state["step"] = 0
[…]

### 2020-04-25 SI/main.py

@@ -14,10 +14,10 @@ from transformers.file_utils import add_start_docstrings, add_start_docstrings_t
 from torch.utils.data import DataLoader, RandomSampler, SequentialSampler, TensorDataset
 from arguments import parse_args
 from tqdm import tqdm, trange
-from collections import OrderedDict 
+from collections import OrderedDict
 
 from transformers import (
-    MODEL_FOR_SEQUENCE_CLASSIFICATION_MAPPING,
+    # MODEL_FOR_SEQUENCE_CLASSIFICATION_MAPPING,
     WEIGHTS_NAME,
     AdamW,
     AutoConfig,
@@ -50,24 +50,20 @@ try:
 except ImportError:
     from tensorboardX import SummaryWriter
 
-
 from utils import convert_dict
 
 n_tasks = 6
-output_dim = 10*n_tasks
+output_dim = 10 * n_tasks
 nb_classes = output_dim
 
 # tf.reset_default_graph()
 
 config = tf.ConfigProto()
-config.gpu_options.allow_growth=True
+config.gpu_options.allow_growth = True
 sess = tf.InteractiveSession(config=config)
 sess.run(tf.global_variables_initializer())
 
-
 logger = logging.getLogger(__name__)
-
-
 
 select = tf.select if hasattr(tf, 'select') else tf.where
 output_mask = tf.Variable(tf.zeros(output_dim), name="mask", trainable=False)
@@ -75,24 +71,24 @@ output_mask = tf.Variable(tf.zeros(output_dim), name="mask", trainable=False)
 
 class BertForSequenceClassification(BertPreTrainedModel):
     def __init__(self, config):
-		super().__init__(config)
-		self.num_labels = config.num_labels
-		self.bert = BertModel(config)
-		self.dropout = nn.Dropout(config.hidden_dropout_prob)
-		self.classifier = nn.Linear(config.hidden_size, self.config.num_labels)
-		self.classifier = self.masked_softmax(self.classifier)
-		self.init_weights()
+        super().__init__(config)
+        self.num_labels = config.num_labels
+        self.bert = BertModel(config)
+        self.dropout = nn.Dropout(config.hidden_dropout_prob)
+        self.classifier = nn.Linear(config.hidden_size, self.config.num_labels)
+        self.classifier = self.masked_softmax(self.classifier)
+        self.init_weights()
 
     @add_start_docstrings_to_callable(BertPreTrainedModel.BERT_INPUTS_DOCSTRING)
[…]

### 2020-05-07 MAS/main.py
modified:   MAS/main.py 	modified:   MAS/mas_utils.py 	modified:   MAS/optimizer_lib.py

@@ -94,14 +94,16 @@ def train(args, train_dataset, task, all_tasks, model, task_num, tokenizer, accu
     optimizer_grouped_parameters = [
         {
             "params": [p for n, p in model.tmodel.named_parameters() if not any(nd in n for nd in no_decay)],
+            "names": [n for n, p in model.tmodel.named_parameters() if not any(nd in n for nd in no_decay)],
             "weight_decay": args.weight_decay,
         },
         {"params": [p for n, p in model.tmodel.named_parameters() if any(nd in n for nd in no_decay)],
+         "names": [n for n, p in model.tmodel.named_parameters() if any(nd in n for nd in no_decay)],
          "weight_decay": 0.0},
     ]
 
+    # optimizer = torch.optim.Adam(optimizer_grouped_parameters, lr=args.init_lr, eps=args.adam_epsilon)
     optimizer = local_AdamW(optimizer_grouped_parameters, args.reg_lambda, lr=args.init_lr, eps=args.adam_epsilon)
-    # scheduler = torch.optim.SGD(optimizer_grouped_parameters, lr=args.init_lr)
     scheduler = get_linear_schedule_with_warmup(
         optimizer, num_warmup_steps=args.warmup_steps, num_training_steps=t_total
     )
@@ -152,14 +154,15 @@ def train(args, train_dataset, task, all_tasks, model, task_num, tokenizer, accu
             # print("************", tr_loss, "*************")
             torch.nn.utils.clip_grad_norm_(model.tmodel.parameters(), args.max_grad_norm)
 
+            # optimizer.step()
             optimizer.step(model.reg_params)
             scheduler.step()  # Update learning rate schedule
             global_step += 1
 
-    optimizer_ft = omega_update_Adam(model.reg_params)
-    print('Updating the omega values for this task')
-    model = compute_omega_grads_norm(model, train_dataloader, optimizer_ft, args.device)
-    sanity_model(model)
+    # optimizer_ft = omega_update_Adam(optimizer_grouped_parameters)
+    # print('Updating the omega values for this task')
+    # model = compute_omega_grads_norm(model, train_dataloader, optimizer_ft, args.device)
+    # sanity_model(model)
 
     if task_num >= 1:
         model = consolidate_reg_params(model)
@@ -422,13 +425,14 @@ def main():
 
     print()
     print("***** Accuracy Matrix *****")
+    print('regularization lambda = {}'.format(args.reg_lambda))
     print()
 
[…]

### 2020-05-07 MAS/mas_utils.py

@@ -33,7 +33,7 @@ def init_reg_params(model, device, freeze_layers=['classifier.weight', 'classifi
     reg_params = dict()
     for name, param in model.tmodel.named_parameters():
         if not name in freeze_layers:
-            print("Initializing omega values for layer", name)
+            # print("Initializing omega values for layer", name)
             omega = torch.zeros(param.size(), dtype=torch.float64)
             omega = omega.to(device)
 
@@ -45,7 +45,7 @@ def init_reg_params(model, device, freeze_layers=['classifier.weight', 'classifi
             param_dict['init_val'] = init_val
 
             # the key for this dictionary is the name of the layer
-            reg_params[param] = param_dict
+            reg_params[name] = param_dict
 
     model.reg_params = reg_params
 
@@ -75,8 +75,8 @@ def sanity_model(model):
 
         print(name)
 
-        if param in model.reg_params:
-            param_dict = model.reg_params[param]
+        if name in model.reg_params:
+            param_dict = model.reg_params[name]
             omega = param_dict['omega']
 
             print("Max omega is", omega.max())
@@ -107,35 +107,35 @@ def init_reg_params_across_tasks(model, device, freeze_layers=['classifier.weigh
     for name, param in model.tmodel.named_parameters():
         if not name in freeze_layers:
 
-            if param in reg_params:
-                param_dict = reg_params[param]
-                print("Initializing the omega values for layer for the new task", name)
+            # if param in reg_params:
+            param_dict = reg_params[name]
+            # print("Initializing the omega values for layer for the new task", name)
 
-                # Store the previous values of omega
-                prev_omega = param_dict['omega']
+            # Store the previous values of omega
+            prev_omega = param_dict['omega']
 
-                # Initialize a new omega
-                new_omega = torch.zeros(param.size())
-                new_omega = new_omega.to(device)
+            # Initialize a new omega
+            new_omega = torch.zeros(param.size())
+            new_omega = new_omega.to(device)
 
-                init_val = param.data.clone()
-                init_val = init_val.to(device)
+            init_val = param.data.clone()
+            init_val = init_val.to(device)
 
-                param_dict['prev_omega'] = prev_omega
-                param_dict['omega'] = new_omega
+            param_dict['prev_omega'] = prev_omega
+            param_dict['omega'] = new_omega
 
-                # store the initial values of the parameters
-                param_dict['init_val'] = init_val
[…]

### 2020-05-07 MAS/optimizer_lib.py

@@ -17,7 +17,8 @@ class local_AdamW(optim.Optimizer):
         correct_bias (bool): can be set to False to avoid correcting bias in Adam (e.g. like in Bert TF repository). Default True.
     """
 
-    def __init__(self, params, reg_lambda, lr=1e-3, betas=(0.9, 0.999), eps=1e-6, weight_decay=0.0, correct_bias=True):
+    def __init__(self, params, reg_lambda, freeze_layers=['classifier.weight', 'classifier.bias'],
+                 lr=1e-3, betas=(0.9, 0.999), eps=1e-6, weight_decay=0.0, correct_bias=True):
         if lr < 0.0:
             raise ValueError("Invalid learning rate: {} - should be >= 0.0".format(lr))
         if not 0.0 <= betas[0] < 1.0:
@@ -29,6 +30,7 @@ class local_AdamW(optim.Optimizer):
         defaults = dict(lr=lr, betas=betas, eps=eps, weight_decay=weight_decay, correct_bias=correct_bias)
         super().__init__(params, defaults)
         self.reg_lambda = reg_lambda
+        self.freeze_layers = freeze_layers
 
     def step(self, reg_params, closure=None):
         """Performs a single optimization step.
@@ -41,7 +43,8 @@ class local_AdamW(optim.Optimizer):
             loss = closure()
 
         for group in self.param_groups:
-            for p in group["params"]:
+            for index, p in enumerate(group["params"]):
+                name = group["names"][index]
                 if p.grad is None:
                     continue
                 grad = p.grad.data
@@ -67,8 +70,9 @@ class local_AdamW(optim.Optimizer):
                 state["step"] += 1
 
                 ###### BEGIN MAS CODE########
-                if p in reg_params:
-                    param_dict = reg_params[p]
+                # if p in reg_params:
+                if name not in self.freeze_layers:
+                    param_dict = reg_params[name]
 
                     omega = param_dict['omega'].cuda()
                     init_val = param_dict['init_val'].cuda()
@@ -123,17 +127,20 @@ class omega_update_Adam(optim.Optimizer):
         correct_bias (bool): can be set to False to avoid correcting bias in Adam (e.g. like in Bert TF repository). Default True.
     """
 
-    def __init__(self, params, lr=1e-3, betas=(0.9, 0.999), eps=1e-6, weight_decay=0.0, correct_bias=True):
[…]

### 2020-05-07 new_SI/arguments.py
new file:   new_SI/arguments.py 	new file:   new_SI/dict_utils.py 	new file:   new_SI/main.py 	new file:   new_SI/mas_utils.py 	new file:   new_SI/my_main.py 	new file:   new_SI/optimizer_lib.py

@@ -1,0 +1,66 @@
+import argparse
+import json
+import torch
+
+def parse_args():
+	parser = argparse.ArgumentParser()
+	parser.add_argument("--data_dir", 
+						type=str,
+						default="../data",
+						required=True,
+						)
+	parser.add_argument("--task_params", 
+						type=str,
+						required=True,
+						help="JSON file path"
+						)
+	parser.add_argument("--output_dir", 
+						type=str,
+						default="./output",
+						required=True,
+						)
+	parser.add_argument("--per_gpu_batch_size", 
+						default=8, 
+						type=int, 
+						help="Batch size per GPU",
+						)
+	parser.add_argument("--cuda", 
+						action="store_true",
+						)
+	parser.add_argument("--tokenizer_name", 
+						type=str,
+						required=True,
+						)
+	parser.add_argument("--do_lower_case", 
+						action="store_true",
+						)
+	parser.add_argument("--model_type",
+						default=None,
+						type=str,
+						required=True,
+						)
+	parser.add_argument("--max_seq_length",
+						default=128,
+						type=int,
+						)
+	parser.add_argument("--num_train_epochs",
+						default=1,
+						type=int,
+						)
+	parser.add_argument("--seed",
+						default=42,
+						type=int,
+						)
+	parser.add_argument('--init_lr', default=0.001, type=float, help='Initial learning rate for training the model')
+	parser.add_argument('--reg_lambda', default=0.01, type=float, help='Regularization parameter')
+
+	args = parser.parse_args()
+	with open(args.task_params) as file:
+		args.task_params = json.load(file)
+	if args.cuda:
+		args.device = torch.device("cuda")
+		args.n_gpu = torch.cuda.device_count()
+	else:
+		args.device = torch.device("cpu")
+		args.n_gpu = 0
+	return args

### 2020-05-07 new_SI/main.py

@@ -1,0 +1,434 @@
+import random
+import numpy as np
+import torch
+import logging
+import os
+import json
+
+from torch.utils.data import DataLoader, RandomSampler, SequentialSampler, TensorDataset
+from arguments import parse_args
+from tqdm import tqdm, trange
+from collections import OrderedDict
+
+from transformers import (
+    WEIGHTS_NAME,
+    AdamW,
+    AutoConfig,
+    AutoModelForSequenceClassification,
+    AutoTokenizer,
+    get_linear_schedule_with_warmup,
+)
+from transformers import glue_compute_metrics as compute_metrics
+from transformers import glue_convert_examples_to_features as convert_examples_to_features
+from transformers import glue_output_modes
+from transformers import glue_processors
+
+try:
+    from torch.utils.tensorboard import SummaryWriter
+except ImportError:
+    from tensorboardX import SummaryWriter
+
+# MAS-SPECIFIC IMPORTS
+from dict_utils import convert_dict
+from mas_utils import init_reg_params, shared_model, exp_lr_scheduler, compute_omega_grads_norm, \
+    init_reg_params_across_tasks, consolidate_reg_params, sanity_model
+from optimizer_lib import omega_update_Adam, local_AdamW
+
+logger = logging.getLogger(__name__)
+
+
+def set_seed(seed, n_gpu):
+    random.seed(seed)
+    np.random.seed(seed)
+    torch.manual_seed(seed)
+    torch.cuda.manual_seed(seed)
+    if n_gpu > 0:
+        torch.cuda.manual_seed_all(seed)
+
+
+def save_model(args, task_num, model):
+    if not os.path.exists(args.output_dir):
+        os.makedirs(args.output_dir)
+
+    task_paramters = OrderedDict()
+    bert_paramters = model.tmodel.state_dict().copy()
+
+    for layer, weights in bert_paramters.items():
+        if layer == "classifier.weight" or layer == 'classifier.bias':
+            task_paramters[layer] = weights
+    del bert_paramters["classifier.weight"]
+    del bert_paramters['classifier.bias']
+
+    torch.save(bert_paramters, os.path.join(args.output_dir, "bert_paramters_" + str(task_num) + ".pt"))
+    torch.save(task_paramters, os.path.join(args.output_dir, "task_paramters_" + str(task_num) + ".pt"))
+
+    print()
+    print("***** Parameters Saved for task", task_num, "*****")
+    print()
+
+
[…]

### 2020-05-07 new_SI/mas_utils.py

@@ -1,0 +1,220 @@
+import torch
+
+
+class shared_model(torch.nn.Module):
+    def __init__(self, model):
+        super(shared_model, self).__init__()
+        self.tmodel = model
+        self.reg_params = {}
+
+    def forward(self, x):
+        return self.tmodel(x)
+
+
+def init_reg_params(model, device, freeze_layers=['classifier.weight', 'classifier.bias']):
+    """
+    Input:
+    1) model: A reference to the model that is being trained
+    2) device: which device to use (GPU or not)
+    3) freeze_layers: A list containing the layers for which omega is not calculated. Useful in the
+        case of computational limitations where computing the importance parameters for the entire model
+        is not feasible
+
+    Output:
+    1) model: A dictionary containing importance weights (omega), init_val (keep a reference
+    to the initial values of the parameters) for all trainable parameters is calculated and the updated
+    model with these reg_params is returned.
+
+
+    Function: Initializes the reg_params for a model for the initial task (task = 1)
+
+    """
+    reg_params = dict()
+    for name, param in model.tmodel.named_parameters():
+        if not name in freeze_layers:
+            print("Initializing omega values for layer", name)
+            prev_wt = param.data.clone()
+            param_dict = {}
+
+            # for first task, omega is initialized to zero
+            param_dict['small_omega'] = torch.zeros(param.size(), dtype=torch.float64)
+            param_dict['big_omega'] = torch.zeros(param.size(), dtype=torch.float64)
+            param_dict['prev_wt'] = prev_wt
+
+            # the key for this dictionary is the name of the layer
+            reg_params[param] = param_dict
+
+    model.reg_params = reg_params
+
+    return model
+
+
+def exp_lr_scheduler(optimizer, epoch, init_lr=0.0008, lr_decay_epoch=20):
+    """
+    Decay learning rate by a factor of 0.1 every lr_decay_epoch epochs.
+    """
+    lr = init_lr * (0.1 ** (epoch // lr_decay_epoch))
+    print('lr is ' + str(lr))
+
+    for param_group in optimizer.param_groups:
+        param_group['lr'] = lr
+
+    return optimizer
+
+
+# sanity check for the model to check if the omega values are getting updated
+def sanity_model(model):
+    for name, param in model.tmodel.named_parameters():
+
+        print(name)
+
+        if param in model.reg_params:
+            param_dict = model.reg_params[param]
+            omega = param_dict['omega']
+
+            print("Max omega is", omega.max())
[…]

### 2020-05-07 new_SI/my_main.py

@@ -1,0 +1,185 @@
+import tensorflow as tf
+import numpy as np
+
+from tensorflow.examples.tutorials.mnist import input_data
+mnist = input_data.read_data_sets("/tmp/", one_hot=True)
+
+
+num_tasks_to_run = 10
+
+num_epochs_per_task = 20
+
+
+# Parameters for the intelligence synapses model.
+param_c = 0.1
+param_xi = 0.1
+
+
+minibatch_size = 64
+learning_rate = 0.001
+
+
+
+def weight_variable(input_size, output_size):
+	return tf.Variable( tf.random_uniform([input_size,output_size], -1.0/np.sqrt(input_size), 1.0/np.sqrt(input_size)) )
+
+
+
+## Network definition -- a simple MLP with 2 hidden layers
+x = tf.placeholder(tf.float32, shape=[None, 784])
+y_tgt = tf.placeholder(tf.float32, shape=[None, 10])
+
+
+# Note: the main paper uses a larger network + dropout; both significantly improve the performance of the system.
+N1 = 400
+N2 = 400
+
+W1 = weight_variable(784,N1)
+b1 = tf.Variable(tf.zeros([1,N1]))
+
+W2 = weight_variable(N1,N2)
+b2 = tf.Variable(tf.zeros([1,N2]))
+
+Wo = weight_variable(N2,10)
+bo = tf.Variable(tf.zeros([1,10]))
+
+
+h1 = tf.nn.relu( tf.matmul(x,W1) + b1 )
+h2 = tf.nn.relu( tf.matmul(h1,W2) + b2 )
+y = tf.nn.softmax( tf.matmul(h2,Wo) + bo )
+
+
+cross_entropy = -tf.reduce_sum( y_tgt*tf.log(y+1e-04) + (1.-y_tgt)*tf.log(1.-y+1e-04) )
+
+optimizer = tf.train.GradientDescentOptimizer(learning_rate)
+
+## Implementation of the intelligent synapses model
+variables = [W1, b1, W2, b2, Wo, bo]
+
+small_omega_var = {}
+previous_weights_mu_minus_1 = {}
+big_omega_var = {}
+aux_loss = 0.0
+
+reset_small_omega_ops = []
+update_small_omega_ops = []
+update_big_omega_ops = []
+for var in variables:
+	small_omega_var[var.op.name] = tf.Variable(tf.zeros(var.get_shape()), trainable=False)
[…]

### 2020-05-07 new_SI/optimizer_lib.py

@@ -1,0 +1,324 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+from __future__ import print_function
+import math
+import torch
+import torch.optim as optim
+
+
+class local_AdamW(optim.Optimizer):
+    """ Implements Adam algorithm with weight decay fix.
+    Parameters:
+        lr (float): learning rate. Default 1e-3.
+        betas (tuple of 2 floats): Adams beta parameters (b1, b2). Default: (0.9, 0.999)
+        eps (float): Adams epsilon. Default: 1e-6
+        weight_decay (float): Weight decay. Default: 0.0
+        correct_bias (bool): can be set to False to avoid correcting bias in Adam (e.g. like in Bert TF repository). Default True.
+    """
+
+    def __init__(self, params, reg_lambda, lr=1e-3, betas=(0.9, 0.999), eps=1e-6, weight_decay=0.0, correct_bias=True):
+        if lr < 0.0:
+            raise ValueError("Invalid learning rate: {} - should be >= 0.0".format(lr))
+        if not 0.0 <= betas[0] < 1.0:
+            raise ValueError("Invalid beta parameter: {} - should be in [0.0, 1.0[".format(betas[0]))
+        if not 0.0 <= betas[1] < 1.0:
+            raise ValueError("Invalid beta parameter: {} - should be in [0.0, 1.0[".format(betas[1]))
+        if not 0.0 <= eps:
+            raise ValueError("Invalid epsilon value: {} - should be >= 0.0".format(eps))
+        defaults = dict(lr=lr, betas=betas, eps=eps, weight_decay=weight_decay, correct_bias=correct_bias)
+        super().__init__(params, defaults)
+        self.reg_lambda = reg_lambda
+
+    def step(self, reg_params, closure=None):
+        """Performs a single optimization step.
+        Arguments:
+            closure (callable, optional): A closure that reevaluates the model
+                and returns the loss.
+        """
+        loss = None
+        if closure is not None:
+            loss = closure()
+
+        for group in self.param_groups:
+            for p in group["params"]:
+                if p.grad is None:
+                    continue
+                grad = p.grad.data
+                zero = torch.FloatTensor(p.data.size()).zero_()
+                if grad.equal(zero.cuda()):
+                    print('omega after zero')
+                if grad.is_sparse:
+                    raise RuntimeError("Adam does not support sparse gradients, please consider SparseAdam instead")
+
+                state = self.state[p]
+
+                # State initialization
[…]

### 2020-05-18 paper/paper.tex
Updates from Overleaf

--- 2020-04-22 paper/paper.tex
@@
 \usepackage[hyperref]{naaclhlt2019}
+\usepackage[utf8]{inputenc}
+\usepackage{graphicx}
+\usepackage{amssymb, amsmath}
+\usepackage{booktabs}
+\usepackage{natbib}
 \usepackage{times}
-\usepackage{latexsym}
-
+\usepackage{latexsym, amsmath}
+% \documentclass{article}
+\usepackage{array,multirow}
 \usepackage{url}
 
-%\aclfinalcopy % Uncomment this line for the final submission
+\aclfinalcopy % Uncomment this line for the final submission
 %\def\aclpaperid{***} %  Enter the acl Paper ID here
@@
 
+%%%%%%%%%%%%%%%%% GUIDELINES %%%%%%%%%%%%%%%
+
+% Final paper rubric  (20 points)
+% This is roughly the same as the above, but adds points for results and analysis, and adds a requirement that the introduction summarizes the results.
+
+% Introduction/overall idea  (7):
+% Clear overall motivation for project  (2)
+% Clear description and motivation for any novel techniques, including baseline results  (2)
+% Clear summary of findings  (3)
+
+% Background  (3):
+% No major omissions from the literature review  (2)
+% 10+ papers cited  (1)
+% 5+ relevant papers discussed in detail, with explanations of how they relate to your project  (1)
+
+% Results and Analysis  (7):
+% Well designed experiments with no unnecessary differences between any models/methods under comparison  (3)
+% Work fully complete, with no easy-to-answer empirical questions left unanswered  (2)
+% Informative, non-trivial error analysis and results writeup  (2)
+
+% Overall writing  (3):
+% Reasonably close fit to ACL style  (1)
+% Readable prose  (2)
+% Collaboration statement  (0, -1 for groups that leave it out) 
+% We reserve the right to redistribute points unevenly between team members in case of very uneven contributions.
+
 \newcommand\BibTeX{B{\sc ib}\TeX}
+\usepackage[ruled,vlined]{algorithm2e}
+\title{Continual NLU: Enabling language models to learn downstream tasks in an online fashion}
 
-\title{Life-long NLU: Continual Learning of Downstream Natural Language Tasks}
-
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\}
-
+\author{{Mohith Damarapati, Govind Mittal, Chandra Prakash Konkimalla}\\
+  {\tt \{md4289, gm2724, cpk290\}@nyu.edu}}
 \date{}
-
 \begin{document}
@@
   Qualified general intelligence has the ability of learning new tasks without immediately becoming worse at an older one.
-With this statement at the core of this paper, we explore various techniques to prevent forgetting in a state-of-the-art language model.
-These techniques range involve Elastic Weight Consolidation, Memory aware synapses and semantic intelligence \cite{french1999catastrophic}
+With this statement at the core of this paper, we explore various techniques to prevent catastrophic forgetting  (CF) in a state-of-the-art language model.
+The paper explores two neuroscience inspired regularization techniques to mitigate CF, \textit{viz.}, Elastic Weight Consolidation and Memory Aware Synapses on pre-trained BERT model.
+Backward transfer is the
+  metric used to evaluate these techniques.
+The paper aims to reduce negative backward transfer on the previously trained tasks.
+As per our knowledge, this is the first work attempting to enable language models to learn downstream tasks in an online fashion and evaluating them based on the metric mentioned above.
 \end{abstract}
+
+% \section{credits
+
+\section{Introduction}
+\label{sec:intro}
+
+Natural cognitive systems gradually forget previously learned information unlike the CF observed in current connectionist approaches \cite{french1999catastrophic}.
+This problem is significant in the domain of natural language understanding  (NLU) as well.
+
+Humans are remarkable at using their previously acquired knowledge when learning a new language task.
+For instance, children first learn a language by mostly observing and listening to their parents.
+They bolster their language skills through curricula by learning more formal language rules like grammar and syntax.
+Using their linguistic knowledge, they can comprehend intricate texts and can answer questions based on them.
+They can even infer meanings of natural language sentences used in complex contexts.
+In all stages of learning, humans are exceptionally good at retaining important parts of their previous knowledge.
+
+In order to design real-world self-learning systems, two requirements are essential -- adaptability to learn new knowledge and stability while evolving and integrating it.
+Therefore, a the ratio of \textit{how plastic} and \textit{how static} a system should be decides how adaptable and how stable it is, respectively.
+A balance needs to be maintained to alleviate the problem of CF of consolidated knowledge, which gives rise to the \textit{stability-plasticity dilemma}.
+
+State-of-the-art deep learning based language models like BERT \cite{DBLP:journals/corr/abs-1810-04805} perform exceptionally well on the NLU tasks.
+However, these models struggle to learn new tasks by retaining previously acquired knowledge \cite{DBLP:journals/corr/abs-1901-11373}.
+Whenever new data becomes available, the model has to be re-trained again on all the previous data.
+Further, it expects our data to be shuffled to perform well.
+Re-training is a costly process and shuffling is not possible in case of scenarios where data comes in a continuous stream.
+
+Current literature evaluates language models based on metrics like accuracy and F1 score on a single task for which it is fine-tuned for.
+We call this as vanilla fine-tuning.
+Vanilla fine-tuning does not measure adaptability of our model to learn new tasks without forgetting the previously acquired knowledge.
+In this paper, we propose a continual learning framework to fine-tune our language models with a capability to adapt to learning new tasks.
+Apart from accuracy and F1 score, our framework also outputs backward transfer \citeauthor{DBLP:journals/corr/Lopez-PazR17} which is a metric to measure the retention capacity.
+We further argue that retaining and reusing the linguistic knowledge and avoiding CF is an important characteristic of general linguistic intelligence.
+
+Our work in this paper mainly focuses on comparing vanilla fine-tuning with continual fine-tuning on BERT-base.
+We incorporate neuroscience inspired techniques like Elastic Weight Consolidation  (EWC, \citealt{DBLP:journals/corr/KirkpatrickPRVD16}) and Memory Aware Synapses  (MAS, \citealt{aljundi2018memory}) into our framework to mitigate CF.
+
+\section{Related Work}
+\label{sec:related}
+
+There has been multiple ways proposed to mitigate CF in connectionist networks. The paper segregates and reviews some of them into the following categories.
+
+\subsection{Memory based methods}
+Memory methods involve \textit{rehearsing} on old samples along with seeing new distribution data alternately \cite{Robins1995CatastrophicFR, Gepperth2016ABI}.
+These methods work best in preventing CF, but the biggest drawback is that they involve storing past events explicitly, which makes it difficult to scale up with time as the neural networks becomes very large and neural resources are limited.
+% which is the case for most state-of-the-art architectures 
+%  (e.g. BERT $\sim$ 340M parameters \cite{DBLP:journals/corr/abs-1810-04805}, FixEfficientNet $\sim$ 480M parameters \cite{touvron2019fixing}, etc). 
+Also, this approach does not consider the fact that a network needs to learn unknown number of future tasks, which makes choosing the \textit{defining set of examples} per task for storing in a fixed resourced system complicated.
+
+\subsection{Regularization based methods}
+These methods alleviates CF by enforcing a cost-based constraint during the update step of the network weights.
+These approaches aim to change a subset or all of the current parameters to an optimal value that works well for both the previous tasks and the current new task.
+
+% \citet{Li2018LearningWF} proposed \textit{Learning without Forgetting  (LwF)} for convolutional neural networks.
+This approach optimizes the new task parameters, while additionally optimizing the predictions made by the shared parameters, does not deviate much from previous predictions.
+The loss function while optimizing for each new parameter, minimizes the difference between new output and old output predictions as though learning the old task again.
+
+% % The following equation illustrates the optimization step used in LwF,
+
+% \begin{equation}
+% \begin{split}
+% \theta^*_s,\theta^*_o,\theta^*_n \leftarrow \text{argmin}_{\hat{\theta}_s,\hat{\theta}_o,\hat{\theta}_n} [ \lambda_o \mathcal{L}_{old} (Y_o,\hat{Y}_o) \\ +
+% \mathcal{L}_{new} (Y_n,\hat{Y}_n) + \mathcal{R} (\hat{\theta}_s,\hat{\theta}_o,\hat{\theta}_n)],
+% \end{split}
+% \end{equation}
+
+% where $\mathcal{L}_{old} (Y_o,\hat{Y}_o)$ and $\mathcal{L}_{new} (Y_n,\hat{Y}_n)$ represent the difference between the predicted values $\hat{Y}$ and the ground truth values $Y$ of the old and new tasks, respectively using parameters $\hat{\theta}_s,\hat{\theta}_o $ and  $\hat{\theta}_n$.
+$\lambda_o$ is used to balance previous and current tasks, and $\mathcal{R}$ is a regularization term to prevent overfitting.
+
+% After the optimization, a new smaller model is trained using knowledge distillation which works optimally as a multi-task model for all learned tasks.
+The requirement of storing data from previous tasks is its biggest disadvantage.
+
+\citet{DBLP:journals/corr/KirkpatrickPRVD16} proposed \textbf{Elastic Weight Consolidation (EWC)} which constrains each parameter based on how important it is to the previous task, which results in model that is flexible for adapting to new tasks while maintaining the performance on previous task.
+Per-parameter significance is calculated using the diagonal of the Fischer information matrix, which is an approximation of the second derivative of loss with respect to each parameter.
+This approximation is linear to compute in the number of parameters and training examples.
+The final parameters are calculated as follows:
+\begin{multline}
+\theta_N^* \leftarrow \text{argmin}_{\theta} L_N (\theta) + \\ \lambda \sum_i \dfrac{1}{2}  (\dfrac{dL_{Pi} (\theta_{Pi})}{d\theta_{Pi}})^2 (\theta - \theta_{Pi})^2 
+\label{eq:ewc}
+\end{multline}
+where $\theta_N^*$ are the optimal parameters after training on new task.
+$L_N (\theta)$ is the loss metric for new task, $dL_{Pi} (\theta_{Pi})$ is the loss metric for previous ($i^{th}$) task, $\theta_{Pi} $ are the optimal parameters until $i^{th}$ task.
+$\lambda$ is a hyper-parameter for measuring the importance of remembering old task parameters.
+
+ \citet{aljundi2018memory} proposed \textbf{Memory Aware Synapses} inspired by Hebbian learning in natural systems.
+The core idea is to learn which parts of the model parameters are important relative to others, using unlabelled data itself.
+They calculate importance weights $\Omega_{ij}$ for all parameters $\theta_{ij}$, where $i$ and $j$ are indices of pairs of neurons $n_i$ and $n_j$ residing in two consecutive layers, respectively.
+The importance weight represent the \textit{sensitivity} of the function output of a learned function, $F:X_n \longrightarrow Y_m$, to changes in the corresponding parameter.
+Therefore,
+ \vspace{-0.3cm}
+\begin{equation}
+\Omega_{ij} =\frac{1}{N}\sum_{k=1}^N  \mid\mid g_{ij} (x_k) \mid\mid
+\label{eq:omega_mas}
+\end{equation}
+where, $N$ is the number of data points at a given stage and
+ \vspace{-0.3cm}
+\begin{equation}
+g_{ij} (x_k)=\frac{\partial  (F (x_k; \theta))}{\partial \theta_{ij}}
+\label{eq:grad_mas}
+\end{equation}
+for a given data point $x_k$.
+Therefore, whichever parameters have lower importance can be changed without degrading the accuracy on previous tasks, while decreasing the loss for subsequent tasks.
+Thus, if we wish to learn a new task, the total loss function $L (\theta)$ becomes,
+\begin{equation}
+    L (\theta)=L_n (\theta)+{\lambda} \sum_{i,j} \Omega_{ij} (\theta_{ij}-\theta^*_{ij})^2
+    \label{eq:mas_loss}
+\end{equation}
+where, $L_n (\theta)$ is the new task loss, $\theta^*_{ij}$ are the old parameters and $\lambda$ is a regularizer hyperparameter.
+\citet{DBLP:journals/corr/ZenkePG17} \textbf{Synaptic Intelligence} loss is similar to MAS: 
+ \begin{align*}
+     L (\theta) &=L_n (\theta)+{\lambda} \sum_{k} \Omega_k^{\mu}  (\theta - \theta_k)^2,\\ 
+    \Omega_k^{\mu} &= \sum_{v<\mu} \dfrac{\omega_k^v}{ (\Delta_k^v)^2+\epsilon} \\
+     \omega_k^v &= \int_{t^{\mu-1}}^{t^{\mu}} g_k (t)\theta^{'}_k (t)
+ \end{align*}
+Here k signifies task number, $g_k (t)$ is the gradient of loss w.r.t parameter k, $\theta^{'}_k (t)$ is the parameter change at time $t$.
+In this case, the importance of parameter is an accumulation of product of gradient and parameter change.
+It depends on two quantities: 1) $ \omega_k^v $ is a drop in loss over the trajectory of training.
+2) How far the loss has changed $\Delta_k^v = \theta_k (t^v) - \theta_k (t^{v-1})$.
+
+\subsection{Dynamic Architectures} 
+Dynamic approaches the problem by augmenting a network as new tasks are encountered and more neural resources are needed \cite{Rusu2016ProgressiveNN, Cortes2017AdaNetAS}.
+Old network parameters are fully preserved to prevent CF and additional neurons are added and trained separately.
+Although this approach works well for reinforcement learning tasks but architecture complexity increases with number of learned tasks.
+% proposed a model augmentation technique named \textit{Progressive Networks}, in which the old network parameters are preserved to prevent CF and when a new task needs to be learned, a new network is trained and coalesced into the old network by forming lateral connections.
+This approach although works well on reinforcement learning tasks, but leads
+
+% \citet{Cortes2017AdaNetAS} proposed a technique similar to neural architectural search named \textit{AdaNet}, in which they optimize both structure and weights of networks starting with a general structure.
+The models adapts itself as newer tasks are learned.
+The approach balances the model complexity by merging similar features to obtain compact feature representations and scaling up when more neural resources are needed.
+
+\section{Proposed Method}
+\label{sec:prop_method}
+
+\subsection{Evaluation Metrics}
+\label{sec:metric}
+Our continual learning framework is evaluated by the following two metrics. They are:
+\begin{enumerate}
+    \item \textit{Backward transfer  (BT)} is the influence of learning a new task on the previous tasks. 
+    % \item \textit{Forward transfer  (FWT)} is the influence of learning a new task on future tasks.
+    \item \textit{Accuracy} is the test classification accuracy on the current new task.
+\end{enumerate}
+
+We define $R$ as the accuracy matrix and $Tr$ as the transfer matrix, where $R_{i, j}$ is the test classification accuracy of the model on task $t_j$ after the previous task $t_i$ and $Tr_{i, j}$ is the backward transfer when $i > j$, respectively.
+
+\subsection{Continual Framework
+\footnote{Code available at - \url{https://github.com/mittalgovind/continual-learning-nlu}.}}
+
+\begin{algorithm}
+    $T \leftarrow \mbox{Tasks}$ \\
+    $N \leftarrow \mbox{Number of Tasks}$ \\
+    $\theta_{B_0} \leftarrow \mbox{Bert Pre-trained Parameters}$\\
+    $R \leftarrow 0_{N \times N}$ \Comment{;Test Accuracy Matrix}\\
+    $Tr \leftarrow 0_{N \times N}$ \Comment{;Transfer Matrix}\\
+  \For{$i = 1:N$}{
+    $D_i \leftarrow data (T_{i, train})$ \\
+    $\theta_{B_i}, \theta'_{T_i}$ \leftarrow $\mbox{argmin}_{\theta_B, \theta_T} L (D_i,  \theta_{B_{i-1}}, \theta_{T_i})$\\
+    \For{$j = 1:N$}{
+        $D_{test} \leftarrow data (T_{j, test})$ \\
+        $R_{i,j} \leftarrow acc (\theta_{Bi}, \theta'_{T_j}, D_{test})$ \\
+        $Tr_{i, j} \leftarrow R_{i, j} - R_{i, i}$ \\
+    }
+    }
+    \textbf{return} $R, Tr$
+    \caption{Proposed Framework}
+    \label{algo:1}
+\end{algorithm}
+
+The paper proposes a continual framework for learning multiple downstream tasks on BERT and illustrates in Algorithm \ref{algo:1}.
+Let $T$ be the tasks to be learned, $N$ be the number of tasks, $\theta_{B_0}$ be BERT pre-trained parameters obtained from huggingface\footnote{https://github.com/huggingface/transformers}, $R$ be the accuracy matrix and $Tr$ be the transfer matrix, both initialized to zero.
+
+Continual fine-tuning procedure involves common BERT parameters and multiple heads.
+First, $T_{1}$ is trained with BERT parameters($\theta_{B_0}$) and a randomly initialized task-specific head ($\theta_{T_1}$) with corresponding loss ($L (D_1,  \theta_{B_{0}}, \theta_{T_1})$).
+Next task $T_2$ is trained with previous BERT parameters($\theta_{B_1}$) and another randomly initialized task-specific head($\theta_{T_2}$) with loss($L (D_2,  \theta_{B_{1}}, \theta_{T_2})$).
+This procedure is repeated for all the remaining tasks.
+Accuracy($R_{i,j}$) is calculated by using $\theta_{B_i}$ and head $\theta'_{T_i}$ with test data ($data (T_{j, test})$), where $\theta'_{T_i}$ are the final task-specific head parameters.
+
+% We fine-tune BERT on $N$ downstream tasks $T_i, \forall i \in [1, N]$.
+During the training loop, the task-specific training data is loaded.
+Let the BERT-specific parameters be $\theta_{B_i}$ after any training task $T_i$.
+When training the next task $T_{i+1}$, a randomly initialized task-specific head with parameters $\theta_{T_{i+1}}$ is attached to previously trained $\theta_{B_{i}}$.
+
+In case of vanilla fine-tuning, all task-specific heads are initialized randomly and BERT-specific parameters  (All BERT parameters except the task specific ones) are re-initialized to $\theta_{B_0}$.
+But, in this framework, BERT-specific parameters  are \textit{not re-initialized}, when training new tasks.
+
+In EWC, we compute mean and Fisher consolidate after training each task.
+Fisher consolidate is computed as a running average instead of accumulating all the gradients by approximating (ref.
+eq.~\ref{eq:ewc}) as given in \citealt{Rao1992}.
+This approximation minimizes the memory complexity of our gradient updates which is important for a feasible implementation of a model, like BERT consisting of $\sim$100M parameters.
+
+In MAS, we use a modified Adam optimizer to access the gradients of each batch (ref.
+eq.~\ref{eq:grad_mas}) and update the corresponding importance weights (ref.
+eq.~\ref{eq:omega_mas}) as running average of the absolute values of per-parameter gradients for a given batch.
+The gradient of each parameter for the current task is added with $2{\lambda} \Omega (\theta-\theta^*)$ (ref.
+eq.~\ref{eq:mas_loss}).
+
+After computing importance weights of each parameter for the current task and finishing training, we consolidate the previously trained weights $\theta_{B_i}$.
+These consolidated previous parameters helps us to retain knowledge obtained from previously learned tasks and are used while learning a new one.
+
+While evaluating the model, test accuracy on task $T_i$ is reported after re-installing its task-specific head.
+After training a task $T_i$, backward transfer for all previous tasks  ($T_j, \forall j<i$) is evaluated.
+Backward transfers are obtained from $R$ and stored in the lower triangle of an $N \times N$ transfer matrix $Tr$.
+These consolidated previous parameters helps us to retain knowledge obtained from previously learned tasks and are used while learning a new one.
+
+\subsection{Data and Base Model}
+\label{sec:data}
+
+All our experiments are performed on GLUE tasks \cite{wang2019glue}.
+We selected two low resource  (MRPC and RTE) and two high resource  (QNLI and SST-2) tasks.
+Results are reported on multiple combinations of two and three tasks.
+
+All our experiments are performed on BERT 
+\footnote{We argue that CF is a problem not specific to language models but to neural networks as a whole.
+In this work we wish to prove that using regularization techniques can alleviate CF.
+Therefore, it justifies using BERT, as the negative backward transfer might remain proportional and serves as a proof-of-concept.}, which can also be extended to more recent language models like RoBERTa \cite{liu2019roberta}, ALBERT \cite{lan2019albert}, etc.
+
+\section{Results and Analysis}
+\label{sec:results}
+\begin{table}[h!]
+    \centering
+    \caption{Low Resource Tasks.
+Representation:  0.87 (-0.48)$\rightarrow$0.64 meant the accuracy was 0.87 after the model is trained on $1^{st}$ task.
+It reduced by 0.48 after training on $2^{nd}$ task and the $2^{nd}$ task accuracy is 0.64.
+}
+    \resizebox{0.9\columnwidth}{!}{
+    \begin{tabular}{|c|c|c|}
+        \hline
+         \textbf{Task} & \textbf{MRPC$\rightarrow$RTE} & \textbf{RTE$\rightarrow$MRPC} \\
+        \hline \hline
+        \textbf{Base} & 0.87 (-0.48)$\rightarrow$0.64 & 0.65 (-0.14)$\rightarrow$0.83\\
+        \hline
+        \textbf{EWC} & 0.86 (-0.00)$\rightarrow$0.65 & 0.65 (-0.09)$\rightarrow$0.86 \\
+        \hline
+        \textbf{MAS} &  0.87 (-0.09)$\rightarrow$0.71 & 0.71 (-0.16)$\rightarrow$0.87 \\
+        \hline
+    \end{tabular}
+    }
+    \label{tab:low_resource_table}
+\end{table}
+
+\vspace{-0.3cm}
+
+\begin{table}[h!]
+    \centering
+     \caption{High Resource Tasks: SST-2 and QNLI}
+    \resizebox{0.9\columnwidth}{!}{
+    \begin{tabular}{|c|c|c|}
+        \hline
+         \textbf{Task} & \textbf{SST-2$\rightarrow$QNLI} & \textbf{QNLI$\rightarrow$SST-2} \\
+        \hline \hline
+        \textbf{Base} & 0.91 (-0.39)$\rightarrow$0.77 & 0.86 (-0.38)$\rightarrow$0.90\\
+        \hline
+        \textbf{EWC} & 0.91 (-0.08)$\rightarrow$0.79 & 0.87 (-0.01)$\rightarrow$0.88 \\
+        \hline
+        \textbf{MAS} &  0.90 (-0.41)$\rightarrow$0.50 & 0.87 (-0.30)$\rightarrow$0.90 \\
+        \hline
+    \end{tabular}
+    }
+
+    \label{tab:high_resource_table}
+\end{table}
+
+\vspace{-0.3cm}
+
+\begin{table}[h!]
+    \centering
+    \caption{Three Tasks: MRPC$\rightarrow$RTE$\rightarrow$SST-2.  *Future transfer (FT) is not considered.}
+    \begin{center}
+    \resizebox{0.9\columnwidth}{!}{
+    \begin{tabular}{| c | c | c | c | } 
+    \hline
+    \textbf{Task} & \textbf{MRPC} & \textbf{RTE} & \textbf{SST-2} &
+    \hline\hline
+
+     & 0.87 & *FT & *FT \\ 
+    \cline{2-4}
+    \textbf{Baseline} & 0.46 (-0.41) & 0.71 & *FT   \\ 
+    \cline{2-4}
+     & 0.43 (-0.44) & 0.5 (-0.21) & 0.91   \\ 
+    \hline\hline
+
+    & 0.88 & *FT & *FT \\ 
+    \cline{2-4}
+    \textbf{EWC} & 0.83 (-0.05) & 0.68 & *FT   \\ 
+    \cline{2-4}
+     & 0.85 (-0.03) & 0.6 (-0.08) & 0.91   \\ 
+    \hline\hline
+
+    & 0.87 & *FT & *FT \\ 
+    \cline{2-4}
+    \textbf{MAS} & 0.64 (-0.33) & 0.65 & *FT   \\ 
+    \cline{2-4}
+     & 0.67 (-0.30) & 0.52 (-0.23) & 0.92   \\ 
+    \hline
+
+    \end{tabular}
+    }
+    \end{center}
+
+    \label{tab:three_tasks}
+\end{table}
+
+\begin{table}[h!]
+    \centering
+    \caption{Three Tasks: MRPC$\rightarrow$SST-2$\rightarrow$RTE.}
+    % \caption{Three Tasks: MRPC$\rightarrow$SST-2$\rightarrow$RTE} \footnote{*Future transfer (FT) is not considered.}. \label{tab:three_tasks_2}
+    \begin{center}
+    \resizebox{0.9\columnwidth}{!}{
+    \begin{tabular}{| c | c | c | c | } 
+    \hline
+    \textbf{Task} & \textbf{MRPC} & \textbf{SST-2} & \textbf{RTE} &
+    \hline\hline
+
+     & 0.87 & *FT & *FT \\ 
+    \cline{2-4}
+    \textbf{Baseline} & 0.41 (-0.46) & 0.91 & *FT   \\ 
+    \cline{2-4}
+     & 0.64 (-0.23) & 0.74 (-0.17) & 0.52   \\ 
+    \hline\hline
+
+    & 0.85 & *FT & *FT \\ 
+    \cline{2-4}
+    \textbf{EWC} & 0.82 (-0.03) & 0.91 & *FT   \\ 
+    \cline{2-4}
+     & 0.85 (-0.00) & 0.9 (-0.01) & 0.63   \\ 
+    \hline\hline
+
+    & 0.86 & *FT & *FT \\ 
+    \cline{2-4}
+    \textbf{MAS} & 0.4 (-0.46) & 0.91 & *FT   \\ 
+    \cline{2-4}
+     & 0.75 (-0.11) & 0.84 (-0.07) & 0.61   \\ 
+    \hline
+    \end{tabular}
+    }
+    \end{center}
+    \vspace{-0.5cm}
+\end{table}
+
+% \vspace{-0.6cm}
+
+% We obtained results for baseline and EWC, for the \textbf{first phase}.
+Our baseline results strengthen our hypothesis that the models suffer from very high negative backward transfer.
+Forward transfer is still low and methods to improve it will be discussed in the future work.
+Table 1 shows the results for both vanilla fine-turning  (baseline) and continual fine-turning with EWC.
+The model trained with EWC has relatively lower negative backward transfer compared to baseline.
+We are expecting to further mitigate negative backward transfer with MAS and SI.
+We performed hyperparameter optimization on all results for EWC by running for each task with different lambdas -  \{5e5, 1e6, 1.5e5, 2e6\} and for MAS the lambdas are  \{150, 200, 250\}.
+The reported results for each task are the best among their lambda and seed settings.
+
+% \vspace{-0.8cm}
+
+The results for the baseline (BERT-base), EWC and MAS for the low resource strengthened our hypothesis that the models suffer from very high negative backward transfer.
+In Table~\ref{tab:low_resource_table}, EWC achieves zero backward transfer for the MRPC$\rightarrow$RTE experiment.
+MAS has higher accuracy for RTE but has a lower negative backward transfer compared to EWC.
+In case of data-intensive tasks (QNLI/SST-2) we can see that the baseline backward transfer is low but the EWC performs significantly better.
+MAS does not perform well on data-intensive tasks  across all tested seeds and lambdas.
+
+In case of three consecutive tasks (MRPC$\rightarrow$RTE$\rightarrow$SST-2), the baseline reduces to random choice accuracy for MRPC and RTE tasks.
+Therefore, the baseline model has catastrophically forgotten the previous tasks and making a random choice.
+For MRPC$\rightarrow$SST-2$\rightarrow$RTE the baseline has better accuracy.
+In both of the three task cases, EWC keeps the negative backward transfer in check.
+
+% Results for second phase final phase will also be shown in the future work. MAS and SI are work in progress.
+
+% \subsection{First Phase}
+
+% Baseline and EWC results are done for first phase. Accuracy and transfer for the first phase configuration  (MRPC - RTE) is shown below. Results are reported after 2 epochs.
+
+% \textbf{Baseline Matrix:}
+
+% \begin{center}
+%  \begin{tabular}{||c c c||} 
+%  \hline
+%  Task & MRPC & RTE  \\ [0.5ex] 
+%  \hline\hline
+%  MRPC & 0.86 (CT) & 0.52 (\textbf{FT} -0.12) \\ 
+%  \hline
+%  RTE & 0.65 (\textbf{BT} -0.21) & 0.64 (CT) \\ [1ex] 
+%  \hline
+% \end{tabular}
+% \end{center}
+
+% \textbf{EWC Matrix:}
+
+% \begin{center}
+
+% \end{center}
+
+% \begin{table}[h!]
+% \centering
+%  \begin{tabular}{|c|c|c|} 
+%  \hline
+%  \textbf{Task} & \textbf{MRPC} & \textbf{RTE}  \\
+%  \hline\hline
+%  & \textit{Baseline} & \\
+%  \hline
+%  \textbf{MRPC} & 0.86 (CT) & 0.52 (FT -0.12) \\ 
+%  \hline
+%  \textbf{RTE} & 0.65 (BT -0.21) & 0.64 (CT) \\ % [1ex] 
+%  \hline
+%  & \textit{EWC} & \\ 
+%  \hline\hline
+%  \textbf{MRPC} & 0.87 (CT) & 0.52 (FT -0.12) \\ 
+%  \hline
+%  \textbf{RTE} & 0.75 (BT -0.12) & 0.64 (CT) \\ %[1ex] 
+%  \hline
+% % \caption{Table A}
+% \end{tabular}
+
+% %  \begin{tabular}{|c|c|c|} 
+% %  \hline
+
+% % % \caption{Table A}
+% % \end{tabular}
+% % % \end{center}
+% \caption{\label{base-table} Results for baseline and EWC; \textbf{CT:} Current Task, \textbf{BT:} Backward Transfer, \textbf{FT:} Forward Transfer. 
+%  }
+% \end{table}
+
+\section{Conclusion}
+
+We present a proof-of-concept that neural networks, like BERT, suffer from catastrophic forgetting.
+In order to amend CF, current models expect shuffled training data and re-training procedures for all the previous tasks while learning a new task.
+Re-training is very costly while shuffling is not possible in the cases when data comes continuously.
+Further, models suffering from it cannot be safely deployed in real-time systems to learn new tasks without the intervention of a deep learning practitioner.
+We proposed a continual learning framework which could replace vanilla fine-tuning to enable language models to learn new tasks in an online fashion.
+While EWC greatly mitigated CF in all cases, but MAS fails to achieve the same benchmark, specially for high resource tasks.
+
+\section{Future Work}
+Backward transfer was the metric we used to evaluate our models, but in order to achieve general linguistic intelligence high future transfer is also expected.
+The solution we proposed can be combined by using few-shot learning techniques like Matching Networks, Model Agnostic Machine Learning (MAML), Prototypical Networks to build more robust language models.
+
+We also worked (and implemented) on Synaptic Intelligence (SI, \citealt{DBLP:journals/corr/ZenkePG17}) but it suffers from gradient explosion problem and therefore has been pushed to future work.
+
+\section*{Availability}
+The code and \LaTeX{} source files are available at \url{https://github.com/mittalgovind/continual-learning-nlu}.
+% \section{Conclusion}
+% \label{sec:conc}
+
+\section*{Collaboration Statement}
+The contributions of the authors, in the same order, are as follows:
+
+\textit{Mohith Damarapati:} Implemented EWC  (Elastic Weight Consolidation) from scratch.
+Designed a framework to evaluate models in a continual way.
+Fixed some crucial bugs that hindered our project progress.
+Ran all the experiments for Baseline.
+
+\textit{Govind Mittal:} Implemented Memory Aware Synapses  (MAS) and Synaptic Intelligence  (SI) for BERT from scratch.
+Wrote the complete related work  (Sec.
+\ref{sec:related}, part of introduction  (Sec.
+\ref{sec:intro}) and paper reviewing.
+
+\textit{Chandra Prakash Konkimalla:} Implemented the baseline framework for fine-tuning the tasks one after another.
+Fixed bugs in EWC  (Elastic Weight Consolidation) training procedure.
+Integrated Baseline and EWC into one code so that the results can be consistent.
+Ran all the experiments for EWC and MAS.
+
+% \section*{Future Work}
 
@@
 
-% Center the title, author's name(s) and affiliation(s) across both
+% Center the title, author's name (s) and affiliation (s) across both
 % columns. Do not use footnotes for affiliations. Do not include the
@@
 % cm from the top of the page, followed by a blank line, then the
-% author's names(s), and the affiliation on the following line. Do not
+% author's names (s), and the affiliation on the following line. Do not
 % use only initials for given names  (middle initials are allowed). Do
